---
title: "ACTwatch Indicator 3.2 - Median Sales Volume of Antimalarial AETDs (Outlets with Sales)"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output: 
  word_document:
    toc: false
    toc_depth: 2
    reference_docx: null
---

## Indicator Definition

**Indicator Group:** Volume - Median antimalarial sales volumes outlets with sales

**Description:** The median sales volume of antimalarial products (in Adult Equivalent Treatment Doses) by antimalarial type and outlet type, among outlets with any antimalarial sales

**Numerator:** Median volume of sales (AETDs) for a specific antimalarial product/category

**Denominator:** Outlets with any antimalarial sales that have volume data available for that product/category

**Disaggregation:** By antimalarial type and outlet type; additional disaggregation by strata if available

**Data Source:** Product data (long format)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                      fig.width = 12, fig.height = 8)

library(tidyverse)
library(survey)
library(openxlsx)
library(forcats)
library(here)
library(data.table)

# Set parameters
if (!exists("country")) stop("Global variable 'country' not found")
if (!exists("year")) stop("Global variable 'year' not found") 

# Configuration matching the Stata analysis structure
indicator_config <- list(
  indicator_id = "3.2",
  title = "Median Sales Volume of Antimalarial AETDs (Outlets with Sales)", 
  description = "Median sales volume of antimalarial products by type and outlet among outlets with sales",
  
  # Analysis settings
  dataset = "product", # Product data in long format
  analysis_type = "volume",
  survey_weight = "wt_alloutlet", # Standard outlet weight for volume analysis
  population_filter = quote(booster == 0 & !is.na(volume) & a3 == 1), # Products with volume data, no booster, outlets with sales
  
  # Outlet types (matching Stata outvars1)
  outlet_dummies = c("private_nonprofit", "private_forprofit", "pharmacy",
                    "laboratory", "drug_store", "total_informal", "total_retail",
                    "wholesale"),
  outlet_labels = list(
    "private_nonprofit" = "Private Not-for-Profit",
    "private_forprofit" = "Private For-Profit", 
    "pharmacy" = "Pharmacy",
    "laboratory" = "Laboratory", 
    "drug_store" = "Drug Store",
    "total_informal" = "Informal (Total)",
    "total_retail" = "Retail (Total)",
    "wholesale" = "Wholesaler"
  ),

  # Volume coverage variables (matching Stata vol_cov)
  volume_vars = c(
    "anyam",              # Any antimalarial
    "anyact",             # Any ACT
    "al",                 # Artemether lumefantrine
    "asaq",               # Artesunate amodiaquine
    "appq",               # Artemisinin piperaquine
    "dhappq",             # Dihydroartemisinin piperaquine
    "arppq",              # Arterolane piperaquine
    "otheract",           # Any other ACT
    "qaact",              # QA ACT
    "qa_all",             # WHO PQ and nationally approved
    "qa_who",             # WHO PQ but not nationally approved
    "qa_nat",             # Nationally approved but not WHO PQ
    "qa_none",            # Not QA or nationally approved
    "nonart",             # Non-artemisinins
    "oralqn",             # Oral quinine
    "cq",                 # Chloroquine
    "sp",                 # Sulfadoxine pyrimethamine
    "spaq",               # Sulfadoxine pyrimethamine amodiaquine
    "nonartoth",          # Other non-artemisinins
    "oartmono",           # Oral artemisinin monotherapy
    "noartmono",          # Non-oral artemisinin monotherapy
    "severe",             # Treatment for severe malaria
    "recas",              # Rectal artesunate
    "injas",              # Injectable artesunate
    "injar",              # Injectable artemether
    "injae",              # Injectable arteether
    "injqn"               # Injectable quinine
  ),
  
  # Product labels for better display
  volume_labels = list(
    "anyam" = "Any antimalarial",
    "anyact" = "Any ACT",
    "al" = "Artemether-lumefantrine",
    "asaq" = "Artesunate-amodiaquine", 
    "appq" = "Artemisinin-piperaquine",
    "dhappq" = "Dihydroartemisinin-piperaquine",
    "arppq" = "Arterolane-piperaquine",
    "otheract" = "Any other ACT",
    "qaact" = "QA ACT",
    "qa_all" = "ACT that is both WHO PQ and nationally approved",
    "qa_who" = "ACT that is WHO PQ but not nationally approved", 
    "qa_nat" = "ACT that is nationally approved but not WHO PQ",
    "qa_none" = "ACT not QA or nationally approved",
    "nonart" = "Non-artemisinins", 
    "oralqn" = "Oral quinine",
    "cq" = "Chloroquine",
    "sp" = "Sulfadoxine-pyrimethamine",
    "spaq" = "Sulfadoxine pyrimethamine amodiaquine",
    "nonartoth" = "Other non-artemisinins",
    "oartmono" = "Oral artemisinin monotherapy",
    "noartmono" = "Non-oral artemisinin monotherapy",
    "severe" = "Treatment for severe malaria",
    "recas" = "Rectal artesunate",
    "injas" = "Injectable artesunate",
    "injar" = "Injectable artemether",
    "injae" = "Injectable arteether", 
    "injqn" = "Injectable quinine"
  ),
  
  # ACT types for focused analysis
  act_types = c("anyact", "al", "asaq", "appq", "dhappq", "arppq", "otheract"),
  
  # Alias for Excel function
  antimalarial_order = c("Any antimalarial", "Any ACT", "Artemether-lumefantrine", 
                         "Artesunate-amodiaquine", "Artemisinin-piperaquine", 
                         "Dihydroartemisinin-piperaquine", "Arterolane-piperaquine", 
                         "Any other ACT", "QA ACT", "ACT that is both WHO PQ and nationally approved", 
                         "ACT that is WHO PQ but not nationally approved", 
                         "ACT that is nationally approved but not WHO PQ", 
                         "ACT not QA or nationally approved", "Non-artemisinins", 
                         "Oral quinine", "Chloroquine", "Sulfadoxine-pyrimethamine", 
                         "Sulfadoxine pyrimethamine amodiaquine", "Other non-artemisinins", 
                         "Oral artemisinin monotherapy", "Non-oral artemisinin monotherapy", 
                         "Treatment for severe malaria", "Rectal artesunate", 
                         "Injectable artesunate", "Injectable artemether", "Injectable arteether", 
                         "Injectable quinine"),
  
  # Output settings
  file_suffix = "Median sales volume of AETDs outlets with sales"
)
```

```{r load_data, include=FALSE}
# Load product data (long format)
data_file <- here("Data", "Final data", 
                  paste0(country, "_", year, "_full_data.csv"))

if (!file.exists(data_file)) {
  stop("Data file not found: ", data_file)
}

product_data <- fread(data_file) %>%
  # Ensure strata variables are character
  mutate(across(any_of(c("strata1", "strata2")), as.character)) %>%
  # Clean up blank but non-missing strata values
  mutate(
    strata1 = dplyr::na_if(strata1, ""),
    strata2 = dplyr::na_if(strata2, "")
  ) %>%
  # Drop if outlet category information is missing (following Stata logic)
  filter(!is.na(outcat2))
```

```{r data_processing, include=FALSE}
# Following Stata logic: ensure outlet variables are coded as 0/1
available_outlet_vars <- intersect(indicator_config$outlet_dummies, names(product_data))

processed_data <- product_data %>%
  # Recode outlet variables (following Stata: recode `x'(.=0) if anyam==1)
  mutate(
    across(all_of(available_outlet_vars), 
           ~ifelse(is.na(.) & anyam == 1, 0, .))
  ) %>%
  # Apply population filter
  filter(!!indicator_config$population_filter)

# Detect strata structure
strata_info <- list()
if ("strata1" %in% names(processed_data) && 
    length(unique(na.omit(processed_data$strata1))) > 1) {
  strata1_values <- unique(na.omit(processed_data$strata1))
  strata1_values <- strata1_values[strata1_values != "" & !is.na(trimws(strata1_values))]
  if (length(strata1_values) > 1) {
    strata_info$strata1 <- list(variable = "strata1", values = strata1_values)
  }
}

if ("strata2" %in% names(processed_data) && 
    length(unique(na.omit(processed_data$strata2))) > 1) {
  strata2_values <- unique(na.omit(processed_data$strata2))
  strata2_values <- strata2_values[strata2_values != "" & !is.na(trimws(strata2_values))]
  if (length(strata2_values) > 1) {
    strata_info$strata2 <- list(variable = "strata2", values = strata2_values)
  }
}

has_strata1 <- "strata1" %in% names(strata_info)
has_strata2 <- "strata2" %in% names(strata_info)
cross_strata_possible <- has_strata1 && has_strata2
```

```{r survey_setup, include=FALSE}
# Setup survey design (following Stata: svyset c4 [pweight=wt_allOutlet], strata(strata) fpc(fpc))
survey_design <- processed_data %>%
  filter(!is.na(!!sym(indicator_config$survey_weight))) %>%
  as_survey_design(
    ids = c4,
    weights = !!sym(indicator_config$survey_weight),
    strata = strata1,  # Using strata1 as primary design strata
    fpc = fpc
  )
```

```{r analysis_functions, include=FALSE}
# Calculate median sales volume using weighted percentiles (standardized output format)
calculate_volume_medians <- function(survey_data, group_vars = NULL) {
  
  results <- tibble()
  
  # Available volume variables in the dataset
  available_volume_vars <- intersect(indicator_config$volume_vars, 
                                    names(survey_data$variables))
  
  # Available outlet variables in the dataset  
  available_outlet_vars <- intersect(indicator_config$outlet_dummies, 
                                    names(survey_data$variables))
  
  for (volume_var in available_volume_vars) {
    for (outlet_var in available_outlet_vars) {
      
      tryCatch({
        if (is.null(group_vars)) {
          # National analysis - following the working sub-analysis pattern
          outlet_data_raw <- survey_data$variables %>%
            filter(!!sym(outlet_var) == 1, 
                   !!sym(volume_var) == 1,
                   !is.na(volume))
          
          if (nrow(outlet_data_raw) > 5) {  # Sufficient observations
            # Use weighted percentiles directly on the raw data
            if (requireNamespace("statar", quietly = TRUE)) {
              percentiles <- statar::pctile(
                outlet_data_raw$volume, 
                probs = c(0.25, 0.50, 0.75),
                wt = outlet_data_raw[[indicator_config$survey_weight]]
              )
              
              result_row <- tibble(
                antimalarial_type = volume_var,  # Standardized name for common Excel function
                outlet_type = outlet_var,
                point_estimate = percentiles[2],  # Median as point estimate
                lower_ci = percentiles[1],        # Q25 as lower bound
                upper_ci = percentiles[3],        # Q75 as upper bound
                sample_size = nrow(outlet_data_raw),
                antimalarial_label = indicator_config$volume_labels[[volume_var]] %||% volume_var,
                outlet_label = indicator_config$outlet_labels[[outlet_var]] %||% outlet_var
              )
              
              results <- bind_rows(results, result_row)
            } else {
              # Fallback to survey package if statar not available
              subset_design <- subset(survey_data, 
                                     !!sym(outlet_var) == 1 & 
                                     !!sym(volume_var) == 1 &
                                     !is.na(volume))
              
              q25 <- svyquantile(~volume, subset_design, quantiles = 0.25, method = "constant")
              q50 <- svyquantile(~volume, subset_design, quantiles = 0.50, method = "constant") 
              q75 <- svyquantile(~volume, subset_design, quantiles = 0.75, method = "constant")
              
              result_row <- tibble(
                antimalarial_type = volume_var,  # Standardized name for common Excel function
                outlet_type = outlet_var,
                point_estimate = as.numeric(q50),  # Median as point estimate
                lower_ci = as.numeric(q25),        # Q25 as lower bound
                upper_ci = as.numeric(q75),        # Q75 as upper bound
                sample_size = nrow(outlet_data_raw),
                antimalarial_label = indicator_config$volume_labels[[volume_var]] %||% volume_var,
                outlet_label = indicator_config$outlet_labels[[outlet_var]] %||% outlet_var
              )
              
              results <- bind_rows(results, result_row)
            }
          }
          
        } else {
          # Strata analysis
          strata_values <- unique(survey_data$variables[[group_vars[1]]])
          strata_values <- strata_values[!is.na(strata_values)]
          
          for (strata_val in strata_values) {
            outlet_data_raw <- survey_data$variables %>%
              filter(!!sym(group_vars[1]) == strata_val,
                     !!sym(outlet_var) == 1, 
                     !!sym(volume_var) == 1,
                     !is.na(volume))
            
            if (nrow(outlet_data_raw) > 5) {
              if (requireNamespace("statar", quietly = TRUE)) {
                percentiles <- statar::pctile(
                  outlet_data_raw$volume, 
                  probs = c(0.25, 0.50, 0.75),
                  wt = outlet_data_raw[[indicator_config$survey_weight]]
                )
                
                result_row <- tibble(
                  antimalarial_type = volume_var,  # Standardized name for common Excel function
                  outlet_type = outlet_var,
                  point_estimate = percentiles[2],  # Median as point estimate
                  lower_ci = percentiles[1],        # Q25 as lower bound
                  upper_ci = percentiles[3],        # Q75 as upper bound
                  sample_size = nrow(outlet_data_raw),
                  antimalarial_label = indicator_config$volume_labels[[volume_var]] %||% volume_var,
                  outlet_label = indicator_config$outlet_labels[[outlet_var]] %||% outlet_var
                )
                
                result_row[[group_vars[1]]] <- as.character(strata_val)
                results <- bind_rows(results, result_row)
              } else {
                # Fallback to survey package
                subset_design <- subset(survey_data, 
                                       !!sym(group_vars[1]) == strata_val &
                                       !!sym(outlet_var) == 1 & 
                                       !!sym(volume_var) == 1 &
                                       !is.na(volume))
                
                q25 <- svyquantile(~volume, subset_design, quantiles = 0.25, method = "constant")
                q50 <- svyquantile(~volume, subset_design, quantiles = 0.50, method = "constant")
                q75 <- svyquantile(~volume, subset_design, quantiles = 0.75, method = "constant")
                
                result_row <- tibble(
                  antimalarial_type = volume_var,  # Standardized name for common Excel function
                  outlet_type = outlet_var,
                  point_estimate = as.numeric(q50),  # Median as point estimate
                  lower_ci = as.numeric(q25),        # Q25 as lower bound
                  upper_ci = as.numeric(q75),        # Q75 as upper bound
                  sample_size = nrow(outlet_data_raw),
                  antimalarial_label = indicator_config$volume_labels[[volume_var]] %||% volume_var,
                  outlet_label = indicator_config$outlet_labels[[outlet_var]] %||% outlet_var
                )
                
                result_row[[group_vars[1]]] <- as.character(strata_val)
                results <- bind_rows(results, result_row)
              }
            }
          }
        }
        
      }, error = function(e) {
        message("Error processing ", volume_var, " in ", outlet_var, ": ", e$message)
      })
    }
  }
  
  return(results)
}

# Calculate footnotes
calculate_footnotes <- function(data, strata1_var = NULL) {
  
  incomplete_criteria <- c(203,204,205,207,208,303,304,305,307,308,309,310)
  
  # Count products with volume data by outlet type
  outlet_counts <- tibble()
  available_outlet_vars <- intersect(indicator_config$outlet_dummies, names(data))
  
  for (outlet_var in available_outlet_vars) {
    outlet_label <- indicator_config$outlet_labels[[outlet_var]] %||% outlet_var
    
    if (is.null(strata1_var)) {
      # National counts
      volume_count <- sum(!is.na(data$volume) & data[[outlet_var]] == 1, na.rm = TRUE)
      
      outlet_counts <- bind_rows(outlet_counts, tibble(
        outlet_type = outlet_var,
        outlet_label = outlet_label,
        volume_products = volume_count
      ))
    } else {
      # Strata counts
      strata_levels <- unique(data[[strata1_var]])
      strata_levels <- strata_levels[!is.na(strata_levels)]
      
      for (strata_val in strata_levels) {
        volume_count <- sum(!is.na(data$volume) & 
                           data[[outlet_var]] == 1 & 
                           data[[strata1_var]] == strata_val, na.rm = TRUE)
        
        outlet_counts <- bind_rows(outlet_counts, tibble(
          outlet_type = outlet_var,
          outlet_label = outlet_label,
          strata = strata_val,
          volume_products = volume_count
        ))
      }
    }
  }
  
  # Count incomplete interviews
  incomplete_count <- sum(!is.na(data$volume) & 
                         data$finalintstat %in% incomplete_criteria, na.rm = TRUE)
  
  # Format footnote
  if (is.null(strata1_var)) {
    volume_text <- paste0(outlet_counts$outlet_label, "=", outlet_counts$volume_products, collapse = "; ")
    total_volume <- sum(!is.na(data$volume))
    return(paste0("Volume data available for ", total_volume, " antimalarial products total. By outlet type: ", 
                  volume_text, ". Incomplete interviews = ", incomplete_count))
  } else {
    footnotes <- list()
    strata_levels <- unique(outlet_counts$strata)
    
    for (strata_val in strata_levels) {
      strata_data <- outlet_counts %>% filter(strata == strata_val)
      volume_text <- paste0(strata_data$outlet_label, "=", strata_data$volume_products, collapse = "; ")
      total_volume <- sum(strata_data$volume_products)
      incomplete_strata <- sum(!is.na(data$volume) & 
                              data[[strata1_var]] == strata_val &
                              data$finalintstat %in% incomplete_criteria, na.rm = TRUE)
      footnotes[[strata_val]] <- paste0("Volume data available for ", total_volume, 
                                        " antimalarial products. By outlet type: ", 
                                        volume_text, ". Incomplete interviews = ", incomplete_strata)
    }
    return(footnotes)
  }
}
```

```{r run_analysis, include=FALSE}
# Initialize results storage
results_list <- list()
footnotes_list <- list()

# 1. National level results
national_results <- calculate_volume_medians(survey_design)
national_footnote <- calculate_footnotes(processed_data)

results_list[["national"]] <- national_results
footnotes_list[["national"]] <- national_footnote

# 2. Strata1 results (if available)
if (has_strata1) {
 strata1_results <- calculate_volume_medians(survey_design, group_vars = "strata1")
 
 if (nrow(strata1_results) > 0) {
   results_list[["strata1"]] <- strata1_results
   footnotes_list[["strata1"]] <- calculate_footnotes(
     processed_data, 
     strata1_var = strata_info$strata1$variable
   )
 }
}

# 3. Strata2 results (if available)
if (has_strata2) {
 strata2_results <- calculate_volume_medians(survey_design, group_vars = "strata2")
 
 if (nrow(strata2_results) > 0) {
   results_list[["strata2"]] <- strata2_results
   footnotes_list[["strata2"]] <- calculate_footnotes(
     processed_data,
     strata1_var = strata_info$strata2$variable
   )
 }
}

# 4. Cross-stratification results (if both strata present)
if (cross_strata_possible) {
  strata1_values <- unique(survey_design$variables$strata1)
  strata1_values <- strata1_values[!is.na(strata1_values)]
  strata2_values <- unique(survey_design$variables$strata2) 
  strata2_values <- strata2_values[!is.na(strata2_values)]
  
  all_cross_results <- tibble()
  
  for (strata1_val in strata1_values) {
    for (strata2_val in strata2_values) {
      subset_condition <- survey_design$variables$strata1 == strata1_val & 
                         survey_design$variables$strata2 == strata2_val &
                         !is.na(survey_design$variables$strata1) &
                         !is.na(survey_design$variables$strata2)
      
      if (sum(subset_condition) > 10) {
        subset_design <- subset(survey_design, subset_condition)
        
        combo_results <- calculate_volume_medians(subset_design)
        
        if (nrow(combo_results) > 0) {
          combo_results$strata1 <- strata1_val
          combo_results$strata2 <- strata2_val
          all_cross_results <- bind_rows(all_cross_results, combo_results)
        }
      }
    }
  }
  
  if (nrow(all_cross_results) > 0) {
    for (strata1_val in strata1_values) {
      strata1_data <- all_cross_results %>% filter(strata1 == strata1_val)
      if (nrow(strata1_data) > 0) {
        cross_id <- paste0("cross_", strata1_val)
        results_list[[cross_id]] <- strata1_data
        
        processed_strata1 <- processed_data %>% filter(strata1 == strata1_val)
        footnotes_list[[cross_id]] <- calculate_footnotes(processed_strata1)
      }
    }
  }
}
```

```{r create_excel_function}
# Create Excel output
source(here("Scripts", "3_Analysis", "create_excel_function.R"))

excel_success <- create_excel_output(
  results_list = results_list,
  footnotes_list = footnotes_list, 
  indicator_config = indicator_config,
  country = country,
  year = year,
  include_antimalarial_col = TRUE
)

if (!excel_success) {
  message("Failed to create Excel file")
} 
```

```{r analysis_summary, results='asis'}
cat("## Analysis Summary\n\n")
cat("**Data Processing:**\n\n")
cat("- Original products in dataset:", nrow(product_data), "\n")
cat("- Products included (with sales, non-booster, volume data):", nrow(processed_data), "\n")
cat("- Survey design: Complex sampling with outlet weights\n")
cat("- Population: Products with volume data from outlets with any antimalarial sales (a3 == 1)\n\n")

cat("**Stratification:**\n\n")
if (length(strata_info) > 0) {
  for (stratum_name in names(strata_info)) {
    stratum <- strata_info[[stratum_name]]
    cat("-", stratum_name, "(", length(stratum$values), "levels):", 
        paste(stratum$values, collapse = ", "), "\n")
  }
  if (cross_strata_possible) {
    cat("- Cross-stratification: Available\n")
  }
  cat("\n")
} else {
  cat("- No stratification variables available\n\n")
}

available_volume_vars <- intersect(indicator_config$volume_vars, names(processed_data))
available_outlet_vars <- intersect(indicator_config$outlet_dummies, names(processed_data))

cat("**Available Products:**", length(available_volume_vars), "antimalarial categories\n")
cat("**Available Outlet Types:**", length(available_outlet_vars), "outlet types\n\n")
```

## Results

### Figure 1: Median Volume by ACT Type (National)

```{r figure_act_national, fig.width=12, fig.height=8}
if ("national" %in% names(results_list) && nrow(results_list[["national"]]) > 0) {
  
  act_by_type <- results_list[["national"]] %>%
    filter(antimalarial_type %in% indicator_config$act_types) %>%
    group_by(antimalarial_type, antimalarial_label) %>%
    summarise(
      point_estimate = median(point_estimate, na.rm = TRUE),
      lower_ci = median(lower_ci, na.rm = TRUE),
      upper_ci = median(upper_ci, na.rm = TRUE),
      .groups = "drop"
    )
  
  if (nrow(act_by_type) > 0) {
    ggplot(act_by_type, aes(x = fct_reorder(antimalarial_label, point_estimate), 
                           y = point_estimate)) +
      geom_col(fill = "#4F81BD", alpha = 0.8) +
      geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +
      geom_text(aes(label = round(point_estimate, 1)),
                hjust = -0.2, size = 3.5) +
      coord_flip() +
      labs(
        title = str_wrap("Median Sales Volume (AETDs) by ACT Type - Outlets with Sales (National)", width = 60),
        x = "ACT Type",
        y = "Median AETDs",
        caption = "Error bars show 25th and 75th percentiles"
      ) +
      theme_minimal(base_size = 14) +
      theme(
        plot.title = element_text(face = "bold"),
        axis.text.y = element_text(size = 11)
      ) +
      expand_limits(y = max(act_by_type$upper_ci, na.rm = TRUE) * 1.1)
  }
}
```

### Figure 2: Median Volume by Outlet Type (Any ACT, National)

```{r figure_outlet_national, fig.width=12, fig.height=8}
if ("national" %in% names(results_list) && nrow(results_list[["national"]]) > 0) {
  
  any_act_by_outlet <- results_list[["national"]] %>%
    filter(antimalarial_type == "anyact")
  
  if (nrow(any_act_by_outlet) > 0) {
    ggplot(any_act_by_outlet, aes(x = fct_reorder(outlet_label, point_estimate), 
                                   y = point_estimate)) +
      geom_col(fill = "#C0504D", alpha = 0.8) +
      geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +
      geom_text(aes(label = round(point_estimate, 1)),
                hjust = -0.2, size = 3.5) +
      coord_flip() +
      labs(
        title = str_wrap("Median Sales Volume (AETDs) of Any ACT by Outlet Type - Outlets with Sales (National)", width = 60),
        x = "Outlet Type",
        y = "Median AETDs",
        caption = "Error bars show 25th and 75th percentiles"
      ) +
      theme_minimal(base_size = 14) +
      theme(
        plot.title = element_text(face = "bold"),
        axis.text.y = element_text(size = 11)
      ) +
      expand_limits(y = max(any_act_by_outlet$upper_ci, na.rm = TRUE) * 1.1)
  }
}
```

\newpage

### Table 1: National Level Results - Median Sales Volume Matrix

```{r table_national_complete, results='asis'}
if ("national" %in% names(results_list) && nrow(results_list[["national"]]) > 0) {
  
  median_volumes <- results_list[["national"]] %>%
    select(antimalarial_label, outlet_label, point_estimate) %>%
    pivot_wider(names_from = outlet_label, values_from = point_estimate, values_fill = NA) %>%
    mutate(across(where(is.numeric), ~round(., 1)))
  
  table_output <- knitr::kable(median_volumes, format = "markdown")
  cat(table_output, sep = "\n")
  cat("\n*", footnotes_list[["national"]], "*\n\n")
  
} else {
  cat("**No national level data available**\n\n")
}
```

## Technical Notes

**Survey Design:** Complex sampling with outlet weights (wt_alloutlet).

**Population:** Products with volume data from outlets with any antimalarial sales (a3 == 1), excluding booster products.

**Analysis Method:** Weighted medians and quartiles (25th, 50th, 75th percentiles) calculated using survey weights. Each product-outlet combination analyzed separately.

**Confidence Intervals:** Interquartile range (25th-75th percentiles) shown as "confidence intervals" for the median.

**Volume Metric:** Adult Equivalent Treatment Doses (AETDs) - standardized measure allowing comparison across different antimalarial formulations.

**Excel Output:** Results exported with separate sheets for each stratification level, with detailed product-by-outlet breakdowns. Point estimate = median, Lower CI = 25th percentile, Upper CI = 75th percentile.

**Footnotes:** Include counts of products with volume data by outlet type and incomplete interview counts.

**Results Structure:**  
- **National:** Overall median volumes across all outlets with sales  
- **Strata1:** Median volumes by primary stratification variable  
- **Strata2:** Median volumes by secondary stratification variable (if present)  
- **Cross-stratification:** Median volumes by strata2 within each level of strata1 (if both present)  

**Key Difference from Indicator 3.1:** This indicator (3.2) restricts analysis to outlets with any antimalarial sales (a3 == 1), providing median volumes among active antimalarial sellers. Indicator 3.1 includes all outlets with volume data regardless of sales status.

---

**Report generated:** `r format(Sys.time(), '%B %d, %Y at %I:%M %p')`
