---
title: "ACTwatch Indicator 1.1 - Market Composition among Antimalarial-Stocking Outlets"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output: 
  word_document:
    toc: false
    toc_depth: 2
    reference_docx: null
---

## Indicator Definition

**Indicator Group:** Market Composition among antimalarial-stocking outlets

**Description:** The distribution (proportion) of outlets of a given type among outlets with at least one antimalarial in stock on the day of the survey

**Numerator:** Number of a given type of outlet with any antimalarial in stock at the time of the survey visit

**Denominator:** Number of outlets with any antimalarial in stock on the day of the survey visit

**Disaggregation:** By outlet type and strata; additional disaggregation by cross-stratification if possible

**Data Source:** Outlet data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                      fig.width = 10, fig.height = 6)


library(tidyverse)
library(survey)
library(openxlsx)
library(forcats)
library(here)
library(data.table)


# Set parameters
if (!exists("country")) stop("Global variable 'country' not found")
if (!exists("year")) stop("Global variable 'year' not found") 

# Configuration matching the indicator config
indicator_config <- list(
  indicator_id = "1.1",
  title = "Market Composition among Antimalarial-Stocking Outlets",
  description = "Distribution (proportion) of outlets of a given type among outlets with at least one antimalarial in stock",
  
  # Analysis settings
  dataset = "outlet",
  analysis_type = "market_composition",  # Add this line
  survey_weight = "wt_marketshare",
  population_filter = quote(st_anyam == 1 & booster == 0),
  
  # Outlet types to include 
  outlet_dummies = c("private_nonprofit", "private_forprofit", "pharmacy",
                    "laboratory",  "drug_store", "total_informal"),
  
  # Outlet labels for better display
  outlet_labels = list(
    "private_nonprofit" = "Private Not-for-Profit",
    "private_forprofit" = "Private For-Profit", 
    "pharmacy" = "Pharmacy",
    "drug_store" = "Drug Store",
    "laboratory" = "Laboratory",
    "total_informal" = "Informal (Total)"
  ),
  
  # Output settings
  file_suffix = "Market Composition among antimalarial-stocking outlets"
)
```

```{r load_data, include=FALSE}
# Load outlet data
data_file <- here("Data", "Final data", 
                  paste0(country, "_", year, "_outlet_data.csv"))

if (!file.exists(data_file)) {
  stop("Data file not found: ", data_file)
}

outlet_data <- fread(data_file) %>%
  # Ensure strata variables are character
  mutate(across(any_of(c("strata1", "strata2")), as.character)) %>%
  # Drop if outlet category information is missing (following Stata logic)
  filter(!is.na(outcat2)) %>% 
  # Clean up blank but non-missing strata values
  mutate(
    strata1 = dplyr::na_if(strata1, ""),      # convert blank strings to NA
    strata2 = dplyr::na_if(strata2, ""))     # same for strata2
```

```{r data_processing, include=FALSE}
# Following Stata logic: ensure only outlets of specified types are included
processed_data <- outlet_data %>%
  # Create temp_tot to identify outlets in our analysis (following Stata logic)
  rowwise() %>%
  mutate(
    temp_tot = if_else(
      any(c_across(all_of(indicator_config$outlet_dummies)) == 1, na.rm = TRUE), 
      1, 0
    )
  ) %>%
  ungroup() %>%
  # Drop outlets not in specified types (following Stata: drop if temp_tot==0)
  filter(temp_tot == 1) %>%
  select(-temp_tot) %>%
  # Recode outlet variables (following Stata: recode `x'(.=0) if st_anyAM==1)
  mutate(
    across(all_of(indicator_config$outlet_dummies), 
           ~ifelse(is.na(.) & st_anyam == 1, 0, .))
  ) %>%
  # Apply population filter
  filter(!!indicator_config$population_filter)

# Detect strata structure
strata_info <- list()
if ("strata1" %in% names(processed_data) && 
    length(unique(na.omit(processed_data$strata1))) > 1) {
  strata1_values <- unique(na.omit(processed_data$strata1))
  # Remove empty strings and whitespace
  strata1_values <- strata1_values[strata1_values != "" & !is.na(trimws(strata1_values))]
  if (length(strata1_values) > 1) {
    strata_info$strata1 <- list(variable = "strata1", values = strata1_values)
  }
}

if ("strata2" %in% names(processed_data) && 
    length(unique(na.omit(processed_data$strata2))) > 1) {
  strata2_values <- unique(na.omit(processed_data$strata2))
  # Remove empty strings and whitespace  
  strata2_values <- strata2_values[strata2_values != "" & !is.na(trimws(strata2_values))]
  if (length(strata2_values) > 1) {
    strata_info$strata2 <- list(variable = "strata2", values = strata2_values)
  }
}

has_strata1 <- "strata1" %in% names(strata_info)
has_strata2 <- "strata2" %in% names(strata_info)
cross_strata_possible <- has_strata1 && has_strata2
```

```{r survey_setup, include=FALSE}
# Setup survey design (following Stata: svyset c4 [pweight=wt_marketShare], strata(strata) fpc(fpc))
survey_design <- processed_data %>%
  filter(!is.na(!!sym(indicator_config$survey_weight))) %>%
  as_survey_design(
    ids = c4,
    weights = !!sym(indicator_config$survey_weight),
    strata = strata1,  # Using strata1 as primary design strata
    fpc = fpc
  )
```

```{r analysis_functions, include=FALSE}
calculate_market_composition <- function(survey_data, group_vars = NULL) {
  
  results <- tibble()
  
  for (outlet_var in indicator_config$outlet_dummies) {
    if (outlet_var %in% names(survey_data$variables)) {
      
      tryCatch({
        if (is.null(group_vars)) {
          # National analysis using svyciprop for better CI estimation
          prop_result <- svyciprop(as.formula(paste0("~", outlet_var)), 
                                  survey_data,
                                  method = "logit")
          
          ci_result <- confint(prop_result, method = "logit")
          total_result <- svytotal(as.formula(paste0("~", outlet_var)), survey_data)
          
          result_row <- tibble(
            outlet_type = outlet_var,
            point_estimate = as.numeric(prop_result) * 100,
            lower_ci = ci_result[1] * 100,
            upper_ci = ci_result[2] * 100,
            n_weighted = as.numeric(total_result),
            sample_size = nrow(survey_data$variables),
            outlet_label = indicator_config$outlet_labels[[outlet_var]] %||% outlet_var
          )
          
          results <- bind_rows(results, result_row)
          
        } else {
          # Strata analysis using svyciprop
          strata_values <- unique(survey_data$variables[[group_vars[1]]])
          strata_values <- strata_values[!is.na(strata_values)]
          
          for (strata_val in strata_values) {
            subset_condition <- survey_data$variables[[group_vars[1]]] == strata_val & 
                               !is.na(survey_data$variables[[group_vars[1]]])
            
            if (sum(subset_condition) > 5) {  # Only if sufficient observations
              subset_design <- subset(survey_data, subset_condition)
              
              prop_result <- svyciprop(as.formula(paste0("~", outlet_var)), 
                                      subset_design,
                                      method = "logit")
              
              ci_result <- confint(prop_result, method = "logit")
              total_result <- svytotal(as.formula(paste0("~", outlet_var)), subset_design)
              
              result_row <- tibble(
                outlet_type = outlet_var,
                point_estimate = as.numeric(prop_result) * 100,
                lower_ci = ci_result[1] * 100,
                upper_ci = ci_result[2] * 100,
                n_weighted = as.numeric(total_result),
                sample_size = sum(subset_condition),
                outlet_label = indicator_config$outlet_labels[[outlet_var]] %||% outlet_var
              )
              
              result_row[[group_vars[1]]] <- as.character(strata_val)
              results <- bind_rows(results, result_row)
            }
          }
        }
        
      }, error = function(e) {
        message("Error processing ", outlet_var, ": ", e$message)
      })
    }
  }
  
  return(results)
}

calculate_footnotes <- function(data, strata1_var = NULL, strata2_var = NULL) {
  
  # Create a temporary column to flag "incomplete" outlets
  data <- data %>%
    dplyr::mutate(incomplete = (finalintstat %in% c(203,204,205,207,208,303,304,305,307,308,309,310)) & st_anyam == 1)
  
  total_sample <- nrow(data)
  total_incomplete <- sum(data$incomplete, na.rm = TRUE)
  
  # Case 1: National
  if (is.null(strata1_var) & is.null(strata2_var)) {
    return(glue::glue(
      "Sample size = {total_sample}; ",
      "Number of outlets that met screening criteria for a full interview ",
      "but did not complete the interview with any AM in stock = {total_incomplete}"
    ))
  }
  
  # Case 2: One-level strata
  if (is.null(strata2_var) | is.null(strata1_var)) {
    strata_var <- if (!is.null(strata1_var)) strata1_var else strata2_var
    
    strata_summary <- data %>%
      filter(!is.na(.data[[strata_var]])) %>% 
      dplyr::group_by(.data[[strata_var]]) %>%
      dplyr::summarise(
        incomplete = sum(incomplete, na.rm = TRUE),
        n = dplyr::n(),
        .groups = "drop"
      )
    
    sizes <- paste0(strata_summary[[strata_var]], " = ", strata_summary$n, collapse = "; ")
    fails <- paste0(strata_summary[[strata_var]], " = ", strata_summary$incomplete, collapse = "; ")
    
    return(glue::glue(
      "Sample sizes: {sizes}; ",
      "Number of outlets that met screening criteria for a full interview ",
      "but did not complete the interview with any AM in stock: {fails}"
    ))
  }
  
  # Case 3: Cross-strata (collapsed to strata1 totals)
  if (!is.null(strata1_var) & !is.null(strata2_var)) {
    strata1_summary <- data %>%
      filter(!is.na(.data[[strata1_var]])) %>% 
      dplyr::group_by(.data[[strata1_var]]) %>%
      dplyr::summarise(
        incomplete = sum(incomplete, na.rm = TRUE),
        n = dplyr::n(),
        .groups = "drop"
      )
    
    footnotes <- strata1_summary %>%
      dplyr::mutate(note = glue::glue(
        "Sample size = {n}; ",
        "Number of outlets that met screening criteria for a full interview ",
        "but did not complete the interview with any AM in stock = {incomplete}"
      )) %>%
      dplyr::pull(note)
    
    names(footnotes) <- strata1_summary[[strata1_var]]
    return(footnotes)
  }
}
```

```{r run_analysis, include=FALSE}
# Initialize results storage
results_list <- list()
footnotes_list <- list()

# 1. National level results
national_results <- calculate_market_composition(survey_design)
national_footnote <- calculate_footnotes(processed_data)

results_list[["national"]] <- national_results
footnotes_list[["national"]] <- national_footnote

# 2. Strata1 results (always present)
if (has_strata1) {
 strata1_results <- calculate_market_composition(survey_design, group_vars = "strata1")
 
 if (nrow(strata1_results) > 0) {
   results_list[["strata1"]] <- strata1_results
   footnotes_list[["strata1"]] <- calculate_footnotes(
     processed_data, 
     strata1_var = strata_info$strata1$variable
   )
 }
}

# 3. Strata2 results (if present)
if (has_strata2) {
 strata2_results <- calculate_market_composition(survey_design, group_vars = "strata2")
 
 if (nrow(strata2_results) > 0) {
   results_list[["strata2"]] <- strata2_results
   footnotes_list[["strata2"]] <- calculate_footnotes(
     processed_data,
     strata2_var = strata_info$strata2$variable
   )
 }
}

# 4. Cross-stratification results (if both strata present)
if (cross_strata_possible) {
  # Get all combinations of strata1 and strata2
  strata1_values <- unique(survey_design$variables$strata1)
  strata1_values <- strata1_values[!is.na(strata1_values)]
  strata2_values <- unique(survey_design$variables$strata2) 
  strata2_values <- strata2_values[!is.na(strata2_values)]
  
  all_cross_results <- tibble()
  
  # Calculate results for each strata1 x strata2 combination
  for (strata1_val in strata1_values) {
    for (strata2_val in strata2_values) {
      # Create subset condition for this combination
      subset_condition <- survey_design$variables$strata1 == strata1_val & 
                         survey_design$variables$strata2 == strata2_val &
                         !is.na(survey_design$variables$strata1) &
                         !is.na(survey_design$variables$strata2)
      
      if (sum(subset_condition) > 5) {  # Only if sufficient observations
        subset_design <- subset(survey_design, subset_condition)
        
        # Calculate for this specific combination
        combo_results <- calculate_market_composition(subset_design)
        
        if (nrow(combo_results) > 0) {
          # Add strata columns
          combo_results$strata1 <- strata1_val
          combo_results$strata2 <- strata2_val
          all_cross_results <- bind_rows(all_cross_results, combo_results)
        }
      }
    }
  }
  
  if (nrow(all_cross_results) > 0) {
    # Split by strata1 values for separate tables
    for (strata1_val in strata1_values) {
      strata1_data <- all_cross_results %>% filter(strata1 == strata1_val)
      if (nrow(strata1_data) > 0) {
        cross_id <- paste0("cross_", strata1_val)
        results_list[[cross_id]] <- strata1_data
        
        processed_strata1 <- processed_data %>% filter(strata1 == strata1_val)
        footnotes_list[[cross_id]] <- calculate_footnotes(processed_strata1)
      }
    }
  }
}

```

```{r create_excel_function}
# Create Excel output with wide format by outlet type  
source(here("Scripts", "3_Analysis", "create_excel_function.R"))

excel_success <- create_excel_output(
  results_list = results_list,
  footnotes_list = footnotes_list, 
  indicator_config = indicator_config,
  country = country,
  year = year,
  include_antimalarial_col = FALSE
)

if (!excel_success) {
  message("Incomplete to create Excel file")
} 
```

```{r analysis_summary, results='asis'}
cat("## Analysis Summary\n\n")
cat("**Data Processing:**\n\n")
cat("- Original outlets surveyed:", nrow(outlet_data), "\n")
cat("- Outlets included in analysis:", nrow(processed_data), "\n")
cat("- Survey design: Complex sampling with market share weights\n\n")

cat("**Stratification:**\n\n")
if (length(strata_info) > 0) {
  for (stratum_name in names(strata_info)) {
    stratum <- strata_info[[stratum_name]]
    cat("-", stratum_name, "(", length(stratum$values), "levels):", 
        paste(stratum$values, collapse = ", "), "\n")
  }
  if (cross_strata_possible) {
    cat("- Cross-stratification: Available\n")
  }
  cat("\n")
} else {
  cat("- No stratification variables available\n\n")
}
```


## Results

```{r figure_size_presets}
overall_base_size = 18
point_estimate_size = 4
```

### Figure 1: National Market Composition

```{r figure_national, fig.width=10, fig.height=6}
if ("national" %in% names(results_list) && nrow(results_list[["national"]]) > 0) {
  
  chart_data <- results_list[["national"]] %>%
    arrange(desc(point_estimate)) %>%
    mutate(outlet_label = fct_reorder(outlet_label, point_estimate))
  
  ggplot(chart_data, aes(x = outlet_label, y = point_estimate)) +
    geom_col(fill = "steelblue", alpha = 0.8) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), 
                  width = 0.2, color = "black") +
    geom_text(aes(y = upper_ci + 2, 
                  label = paste0("(", round(point_estimate, 1), "%)")),
              hjust = 0, size = point_estimate_size, color = "black") +
    coord_flip() +
    labs(
      title = str_wrap("Market Composition among Antimalarial-Stocking Outlets - National", width = 50),
      x = "Outlet Type",
      y = "Percentage of Total Market (%)",
      caption = "Error bars show 95% confidence intervals. Values in parentheses show point estimates."
    ) +
    theme_minimal(base_size = overall_base_size) +
    theme(
      plot.title = element_text(face = "bold")
    ) +
    scale_y_continuous(limits = c(0, 109), expand = c(0, 0))
  
} else {
  cat("No national data available for charting")
}
```

### Figure 2: Market Composition by Strata1

```{r figure_strata1, fig.width=12, fig.height=8}
if ("strata1" %in% names(results_list) && nrow(results_list[["strata1"]]) > 0) {
  
  strata1_data <- results_list[["strata1"]]
  
  ggplot(strata1_data, aes(x = fct_reorder(outlet_label, point_estimate), 
                          y = point_estimate, fill = strata1)) +
    geom_col(position = "dodge", alpha = 0.8) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), 
                  position = position_dodge(width = 0.9), width = 0.2) +
    geom_text(aes(y = upper_ci + 2, 
              label = paste0("(",round(point_estimate, 1), "%)")),
              hjust = 0, size = point_estimate_size, position = position_dodge(width = 0.9)) +
    coord_flip() +
    labs(
      title = str_wrap("Market Composition by Outlet Type and Strata1", width=50),
      x = "Outlet Type",
      y = "Percentage of Market (%)",
      fill = "Strata1",
      caption = "Error bars show 95% confidence intervals"
    ) +
    theme_minimal(base_size = overall_base_size) +
    theme(
      plot.title = element_text(size = rel(1.1), face = "bold"),
      axis.text = element_text(size = rel(0.9)),
      axis.title = element_text(size = rel(1.0)),
      legend.position = "bottom") +
    scale_fill_brewer(type = "qual", palette = "Set1") +
    scale_y_continuous(limits = c(0, 109), expand = c(0, 0))
}
```

`r if(has_strata2) "### Figure 3: Market Composition by Strata2"`

```{r figure_strata2, fig.width=12, fig.height=8}
if ("strata2" %in% names(results_list) && nrow(results_list[["strata2"]]) > 0) {
  
  strata2_data <- results_list[["strata2"]]
  
  ggplot(strata2_data, aes(x = fct_reorder(outlet_label, point_estimate), 
                          y = point_estimate, fill = strata2)) +
    geom_col(position = "dodge", alpha = 0.8) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), 
                  position = position_dodge(width = 0.9), width = 0.2) +
    geom_text(aes(y = upper_ci + 2, 
              label = paste0("(",round(point_estimate, 1), "%)")),
              hjust = 0, size = point_estimate_size, position = position_dodge(width = 0.9)) +
    coord_flip() +
    labs(
      title = str_wrap("Market Composition by Outlet Type and Strata2", width=50),
      x = "Outlet Type", 
      y = "Percentage of Market (%)",
      fill = "Strata2",
      caption = "Error bars show 95% confidence intervals"
    ) +
    theme_minimal(base_size = overall_base_size) +
    theme(
      plot.title = element_text(size = rel(1.1), face = "bold"),
      axis.text = element_text(size = rel(0.9)),
      axis.title = element_text(size = rel(1.0)),
      legend.position = "bottom") +
    scale_fill_brewer(type = "qual", palette = "Set1") +
    scale_y_continuous(limits = c(0, 109), expand = c(0,0)) 
}
```

`r if(cross_strata_possible) "### Figure 4: Market Composition by Cross-Stratification"`

```{r figure_cross_strata, fig.width=14, fig.height=10}
if (cross_strata_possible) {
  cross_results <- names(results_list)[grepl("^cross_", names(results_list))]
  
  if (length(cross_results) > 0) {
    # Combine all cross-stratification results for plotting
    all_cross_data <- tibble()
    
    for (cross_name in cross_results) {
      cross_data <- results_list[[cross_name]] %>%
        mutate(strata1_group = gsub("cross_", "", cross_name))
      all_cross_data <- bind_rows(all_cross_data, cross_data)
    }
    
    if (nrow(all_cross_data) > 0) {
      ggplot(all_cross_data, aes(x = fct_reorder(outlet_label, point_estimate), 
                                y = point_estimate, fill = strata2)) +
        geom_col(position = "dodge", alpha = 0.8) +
        geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), 
                      position = position_dodge(width = 0.9), width = 0.2) +
        geom_text(aes(y = upper_ci + 2, 
              label = paste0("(",round(point_estimate, 1), "%)")),
              hjust = 0, size = point_estimate_size, position = position_dodge(width = 0.9)) +
        facet_wrap(~strata1_group, scales = "fixed") +
        coord_flip() +
        labs(
          title = str_wrap("Market Composition by Outlet Type and Cross-Stratification", width=50),
          x = "Outlet Type", 
          y = "Percentage of Market (%)",
          fill = "Strata2",
          caption = "Error bars show 95% confidence intervals"
        ) +
        theme_minimal(base_size = overall_base_size) +
        theme(
          plot.title = element_text(size = rel(1.1), face = "bold"),
          axis.text = element_text(size = rel(0.9)),
          axis.title = element_text(size = rel(1.0)),
          legend.position = "bottom",
              strip.text = element_text(face = "bold")) +
        scale_fill_brewer(type = "qual", palette = "Set1") +
        scale_y_continuous(limits = c(0, 109), expand = c(0, 0))
  }
  }
}
```


#### Table 1: National Level Results

```{r table_national, results='asis'}
if ("national" %in% names(results_list) && nrow(results_list[["national"]]) > 0) {
  
  table_data <- results_list[["national"]] %>%
    arrange(desc(point_estimate)) %>%
    select(
      "Outlet Type" = outlet_label,
      "Point Estimate (%)" = point_estimate,
      "Lower CI (%)" = lower_ci,
      "Upper CI (%)" = upper_ci
    ) %>%
    mutate(
      across(contains("%"), ~round(., 2))
    )
  
  table_output <- knitr::kable(table_data, format = "markdown")
  cat(table_output, sep = "\n")
  cat("\n")
  cat("*", footnotes_list[["national"]], "*\n\n")
  
} else {
  cat("**No national level data available**\n\n")
}
```

\newpage 

## Technical Notes

**Survey Design:** Complex sampling with market share weights (`wt_marketshare`), cluster sampling (c4), stratification (strata1), and finite population correction (fpc).

**Population Filter:** Analysis limited to outlets with at least one antimalarial in stock (`st_anyam == 1`) and excluding booster samples (`booster == 0`).

**Statistical Method:** Survey-weighted proportions with 95% confidence intervals using proper subpopulation analysis methods.

**Results Structure:**  
- **National:** Overall market composition across all outlets  
- **Strata1:** Market composition by primary stratification variable (always present)  
- **Strata2:** Market composition by secondary stratification variable (if present and has variation)    
- **Cross-stratification:** Market composition by strata2 within each level of strata1 (if both strata present)  

**Excel Output:** Results exported to Excel workbook with separate sheets for each analysis level.

---

**Report generated:** `r format(Sys.time(), '%B %d, %Y at %I:%M %p')`
