---
title: "ACTwatch Indicator 4.2 - Market Share of Malaria Blood Testing"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output: 
  word_document:
    toc: false
    toc_depth: 2
    reference_docx: null
---

## Indicator Definition

**Indicator Group:** Market share of malaria blood testing

**Description:** Total volume of malaria blood test products sold/distributed across outlet types

**Numerator:** Estimated total volume of diagnostic products of a given type sold/distributed in outlets of a given type

**Denominator:** N/A (absolute volumes reported with confidence intervals, not proportions)

**Disaggregation:** By diagnostic type and outlet type; by strata; by urban/rural

**Data Source:** Product data (long format) - RDT/diagnostic dataset

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                      fig.width = 12, fig.height = 8)

library(tidyverse)
library(survey)
library(openxlsx)
library(forcats)
library(here)
library(data.table)

# Set parameters
if (!exists("country")) stop("Global variable 'country' not found")
if (!exists("year")) stop("Global variable 'year' not found") 

# Configuration matching the Stata analysis structure
indicator_config <- list(
  indicator_id = "4.2",
  title = "Market Share of Malaria Blood Testing",
  description = "Total volume of diagnostic products by type and outlet",
  
  # Analysis settings
  dataset = "product", # Product data in long format (RDT/diagnostic data)
  analysis_type = "market_share",
  survey_weight = "wt_marketshare", # Market share weight (note capital S)
  population_filter = quote(booster == 0), # No booster samples
  
  # Outlet types (matching Stata outvars4 - needs customization)
  outlet_dummies = c("private_nonprofit", "private_forprofit", "pharmacy",
                    "laboratory", "drug_store", "total_informal", "total_retail"),
  outlet_labels = list(
    "private_nonprofit" = "Private Not-for-Profit",
    "private_forprofit" = "Private For-Profit", 
    "pharmacy" = "Pharmacy",
    "laboratory" = "Laboratory", 
    "drug_store" = "Drug Store",
    "total_informal" = "Informal (Total)",
    "total_retail" = "Retail (Total)"
  ),

  # Volume coverage variables for diagnostics (matching Stata dvol_cov)
  volume_vars = c(
    "total",              # Any diagnostic/blood test
    "microscopy",         # Microscopy
    "rdt_true"            # Any RDT
  ),
  
  # Product labels for better display
  volume_labels = list(
    "total" = "Any malaria blood test",
    "microscopy" = "Microscopy",
    "rdt_true" = "Rapid diagnostic test (RDT)"
  ),
  
  # ACT types for focused analysis
  act_types = c("anyact", "al", "asaq", "appq", "dhappq", "arppq", "otheract"),
  
  # Antimalarial ordering for tables
  antimalarial_order = c(
    "Any antimalarial", "Any ACT",
    "Artemether-lumefantrine", "Artesunate-amodiaquine", 
    "Artemisinin-piperaquine", "Dihydroartemisinin-piperaquine",
    "Arterolane-piperaquine", "Any other ACT",
    "QA ACT", "ACT that is both WHO PQ and nationally approved",
    "ACT that is WHO PQ but not nationally approved",
    "ACT that is nationally approved but not WHO PQ",
    "ACT not QA or nationally approved",
    "Non-artemisinins", "Oral quinine", "Chloroquine",
    "Sulfadoxine-pyrimethamine", "Sulfadoxine pyrimethamine amodiaquine",
    "Other non-artemisinins",
    "Oral artemisinin monotherapy", "Non-oral artemisinin monotherapy",
    "Treatment for severe malaria", "Rectal artesunate",
    "Injectable artesunate", "Injectable artemether", 
    "Injectable arteether", "Injectable quinine"
  ),
  
  # Output settings
  file_suffix = "Market share of malaria blood testing"
)

# Source the create_excel_function
source(here("Scripts", "3_Analysis", "create_excel_function.R"))
```

```{r load_data, include=FALSE}
# Load product data (long format) - RDT/diagnostic dataset
data_file <- here("Data", "Final data", 
                  paste0(country, "_", year, "_rdt_micro_data.csv"))

if (!file.exists(data_file)) {
  stop("Data file not found: ", data_file)
}

product_data <- fread(data_file) %>%
  # Ensure strata variables are character
  mutate(across(any_of(c("strata1", "strata2")), as.character)) %>%
  # Clean up blank but non-missing strata values
  mutate(
    strata1 = dplyr::na_if(strata1, ""),
    strata2 = dplyr::na_if(strata2, "")
  ) %>%
  # Drop if outlet category information is missing (following Stata logic)
  filter(!is.na(outcat2))
```

```{r}

print(paste("Initial data:", nrow(product_data)))

# After outcat2 filter
temp1 <- product_data %>% filter(!is.na(outcat2))
print(paste("After outcat2 filter:", nrow(temp1)))

# After booster filter
temp2 <- temp1 %>% filter(booster == 0)
print(paste("After booster filter:", nrow(temp2)))

# Count pharmacy observations with volume
temp3 <- temp2 %>% filter(pharmacy == 1, !is.na(volume))
print(paste("Pharmacy with volume:", nrow(temp3)))
```


```{r data_processing, include=FALSE}
# Following Stata logic: ensure outlet variables are coded as 0/1
available_outlet_vars <- intersect(indicator_config$outlet_dummies, names(product_data))

# Following Stata logic: recode volume product variables (0 = missing for analysis)
# This ensures zero volume products are coded to missing
available_volume_vars <- intersect(indicator_config$volume_vars, names(product_data))

processed_data <- product_data %>%
  # Recode outlet variables (following Stata: recode `x'(.=0) if total==1)
  # mutate(
  #   across(all_of(available_outlet_vars), 
  #          ~ifelse(is.na(.) & total == 1, 0, .))
  # ) %>%
  # Apply population filter
  filter(!!indicator_config$population_filter) %>%
  # Recode volume variables: 0 -> NA (following Stata: recode `x' (0 = .))
  mutate(
    across(all_of(available_volume_vars),
           ~ifelse(. == 0, NA, .))
  )

# Detect strata structure
strata_info <- list()
if ("strata1" %in% names(processed_data) && 
    length(unique(na.omit(processed_data$strata1))) > 1) {
  strata1_values <- unique(na.omit(processed_data$strata1))
  strata1_values <- strata1_values[strata1_values != "" & !is.na(trimws(strata1_values))]
  if (length(strata1_values) > 1) {
    strata_info$strata1 <- list(variable = "strata1", values = strata1_values)
  }
}

if ("strata2" %in% names(processed_data) && 
    length(unique(na.omit(processed_data$strata2))) > 1) {
  strata2_values <- unique(na.omit(processed_data$strata2))
  strata2_values <- strata2_values[strata2_values != "" & !is.na(trimws(strata2_values))]
  if (length(strata2_values) > 1) {
    strata_info$strata2 <- list(variable = "strata2", values = strata2_values)
  }
}

has_strata1 <- "strata1" %in% names(strata_info)
has_strata2 <- "strata2" %in% names(strata_info)
cross_strata_possible <- has_strata1 && has_strata2
```

```{r survey_setup, include=FALSE}
# Setup survey design (following Stata: svyset c4 [pweight=wt_marketShare], strata(strata) fpc(fpc))
survey_design <- processed_data %>%
  filter(!is.na(!!sym(indicator_config$survey_weight))) %>%
  as_survey_design(
    ids = c4,
    weights = !!sym(indicator_config$survey_weight),
    strata = strata1,  # Using strata1 as primary design strata
    fpc = fpc
  )
```

```{r analysis_functions, include=FALSE}
# Calculate single antimalarial-outlet market share
calculate_market_share <- function(survey_data, antimalarial_var, outlet_var) {
  
  # Build filter condition
  filter_condition <- paste0(antimalarial_var, " == 1 & ", outlet_var, " == 1 & !is.na(volume)")
  
  # Check if we have any observations
  n_obs <- nrow(survey_data$variables %>% filter(eval(parse(text = filter_condition))))
  
  if (n_obs == 0) {
    return(tibble(
      antimalarial_type = antimalarial_var,
      outlet_type = outlet_var,
      point_estimate = 0,
      lower_ci = NA_real_,
      upper_ci = NA_real_,
      sample_size = 0
    ))
  }
  
  # Create subset for analysis
  subset_design <- subset(survey_data, eval(parse(text = filter_condition)))
  
  tryCatch({
    # Calculate total volume (following Stata: svy: total volume)
    volume_result <- svytotal(~volume, subset_design, na.rm = TRUE)
    
    # Extract confidence interval
    ci_result <- confint(volume_result)
    
    return(tibble(
      antimalarial_type = antimalarial_var,
      outlet_type = outlet_var,
      point_estimate = as.numeric(volume_result),
      lower_ci = max(ci_result[1], 0),  # Following Stata: if lower < 0, set to 0
      upper_ci = ci_result[2],
      sample_size = n_obs
    ))
    
  }, error = function(e) {
    return(tibble(
      antimalarial_type = antimalarial_var,
      outlet_type = outlet_var,
      point_estimate = 0,
      lower_ci = NA_real_,
      upper_ci = NA_real_,
      sample_size = n_obs
    ))
  })
}

# Calculate all antimalarial-outlet combinations (with optional strata grouping)
calculate_all_market_shares <- function(survey_data, group_vars = NULL) {
  
  results <- tibble()
  
  # Available antimalarial and outlet variables
  available_antimalarials <- intersect(indicator_config$volume_vars, 
                                      names(survey_data$variables))
  available_outlets <- intersect(indicator_config$outlet_dummies, 
                                names(survey_data$variables))
  
  if (is.null(group_vars)) {
    # National level - no grouping
    for (antimalarial in available_antimalarials) {
      for (outlet in available_outlets) {
        
        result <- calculate_market_share(survey_data, antimalarial, outlet)
        
        # Add labels
        result <- result %>%
          mutate(
            antimalarial_label = indicator_config$volume_labels[[antimalarial]] %||% antimalarial,
            outlet_label = indicator_config$outlet_labels[[outlet]] %||% outlet
          )
        
        results <- bind_rows(results, result)
      }
    }
    
  } else {
    # Strata analysis - loop through each strata value (like 3.1 does)
    strata_values <- unique(survey_data$variables[[group_vars[1]]])
    strata_values <- strata_values[!is.na(strata_values)]
    
    for (strata_val in strata_values) {
      # Subset survey design to this strata using bracket notation (avoids !!sym issues)
      strata_subset <- subset(survey_data, 
                             survey_data$variables[[group_vars[1]]] == strata_val)
      
      # Calculate for each antimalarial-outlet combination
      for (antimalarial in available_antimalarials) {
        for (outlet in available_outlets) {
          
          result <- calculate_market_share(strata_subset, antimalarial, outlet)
          
          # Add the strata column (key fix - like 3.1 line 315)
          result[[group_vars[1]]] <- as.character(strata_val)
          
          # Add labels
          result <- result %>%
            mutate(
              antimalarial_label = indicator_config$volume_labels[[antimalarial]] %||% antimalarial,
              outlet_label = indicator_config$outlet_labels[[outlet]] %||% outlet
            )
          
          results <- bind_rows(results, result)
        }
      }
    }
  }
  
  return(results)
}
```


```{r footnotes_function, include=FALSE}
# Generate footnotes (following Stata footnote generation logic)
generate_footnotes <- function(data, filter_vars = NULL) {
  
  # Apply filter if provided
  if (!is.null(filter_vars)) {
    for (var_name in names(filter_vars)) {
      data <- data %>% filter(!!sym(var_name) == filter_vars[[var_name]])
    }
  }
  
  footnote_parts <- character()
  
  # Overall volume count
  total_count <- data %>% 
    filter(!is.na(volume)) %>% 
    nrow()
  
  footnote_parts <- c(footnote_parts, 
                     paste0("Total diagnostic products with volume data = ", total_count))
  
  # By outlet type
  outlet_counts <- character()
  for (outlet in indicator_config$outlet_dummies) {
    if (outlet %in% names(data)) {
      outlet_label <- indicator_config$outlet_labels[[outlet]] %||% outlet
      outlet_count <- data %>%
        filter(!!sym(outlet) == 1 & !is.na(volume)) %>%
        nrow()
      outlet_counts <- c(outlet_counts, 
                        paste0(outlet_label, " = ", outlet_count))
    }
  }
  
  if (length(outlet_counts) > 0) {
    footnote_parts <- c(footnote_parts,
                       paste0("By outlet type: ", paste(outlet_counts, collapse = "; ")))
  }
  
  # Incomplete interviews (following Stata logic)
  if ("finalIntStat" %in% names(data)) {
    incomplete_count <- data %>%
      filter(finalIntStat %in% c(203,204,205,207,208,303,304,305,307,308,309,310) & 
             !is.na(volume)) %>%
      nrow()
    
    if (incomplete_count > 0) {
      footnote_parts <- c(footnote_parts,
                         paste0("Products with volume data from outlets that met screening ",
                               "criteria but did not complete interview = ", incomplete_count))
    }
  }
  
  return(paste(footnote_parts, collapse = ". "))
}
```

```{r run_analysis, include=FALSE}
# Initialize results storage
results_list <- list()
footnotes_list <- list()

# 1. National level results
cat("Calculating national results...\n")
national_results <- calculate_all_market_shares(survey_design)
national_footnote <- generate_footnotes(processed_data)

results_list[["national"]] <- national_results
footnotes_list[["national"]] <- national_footnote

# 2. Strata1 results (if available)
if (has_strata1) {
  cat("Calculating strata1 results...\n")
  strata1_results <- calculate_all_market_shares(survey_design, group_vars = "strata1")
  
  if (nrow(strata1_results) > 0) {
    results_list[["strata1"]] <- strata1_results
    footnotes_list[["strata1"]] <- "Results by primary stratification variable"
  }
}

# 3. Strata2 results (if available)
if (has_strata2) {
  cat("Calculating strata2 results...\n")
  strata2_results <- calculate_all_market_shares(survey_design, group_vars = "strata2")
  
  if (nrow(strata2_results) > 0) {
    results_list[["strata2"]] <- strata2_results
    footnotes_list[["strata2"]] <- "Results by secondary stratification variable"
  }
}

# 4. Cross-stratification results (if both strata present)
if (cross_strata_possible) {
  cat("Calculating cross-stratification results...\n")
  
  strata1_values <- unique(survey_design$variables$strata1)
  strata1_values <- strata1_values[!is.na(strata1_values)]
  strata2_values <- unique(survey_design$variables$strata2)
  strata2_values <- strata2_values[!is.na(strata2_values)]
  
  all_cross_results <- tibble()
  
  for (strata1_val in strata1_values) {
    for (strata2_val in strata2_values) {
      subset_condition <- survey_design$variables$strata1 == strata1_val & 
                         survey_design$variables$strata2 == strata2_val &
                         !is.na(survey_design$variables$strata1) &
                         !is.na(survey_design$variables$strata2)
      
      if (sum(subset_condition) > 10) {  # Need sufficient observations
        subset_design <- subset(survey_design, subset_condition)
        
        combo_results <- calculate_all_market_shares(subset_design)
        
        if (nrow(combo_results) > 0) {
          combo_results$strata1 <- strata1_val
          combo_results$strata2 <- strata2_val
          all_cross_results <- bind_rows(all_cross_results, combo_results)
        }
      }
    }
  }
  
  if (nrow(all_cross_results) > 0) {
    for (strata1_val in strata1_values) {
      strata1_data <- all_cross_results %>% filter(strata1 == strata1_val)
      if (nrow(strata1_data) > 0) {
        cross_id <- paste0("cross_", strata1_val)
        results_list[[cross_id]] <- strata1_data
        
        processed_strata1 <- processed_data %>% filter(strata1 == strata1_val)
        footnotes_list[[cross_id]] <- generate_footnotes(processed_strata1)
      }
    }
  }
}

cat("Analysis complete\n")
```

```{r excel_output, include=FALSE}
# Use the standard create_excel_output function
excel_success <- create_excel_output(
  results_list = results_list,
  footnotes_list = footnotes_list, 
  indicator_config = indicator_config,
  country = country,
  year = year,
  include_antimalarial_col = TRUE
)

if (excel_success) {
  cat("Excel file created successfully\n")
} else {
  cat("Warning: Excel file creation encountered issues\n")
}
```

## Results

#### Figure: Total Diagnostic Volume Distribution by Test Type (National)

```{r figure_diagnostic_volume_national, fig.width=10, fig.height=6}
if ("national" %in% names(results_list) && nrow(results_list[["national"]]) > 0) {
  
  # Get available diagnostic types from actual data
  available_diagnostic_types <- intersect(indicator_config$volume_vars, unique(results_list[["national"]]$antimalarial_type))
  
  # Focus on diagnostic types and aggregate across outlets
  diagnostic_volume_data <- results_list[["national"]] %>%
    filter(antimalarial_type %in% available_diagnostic_types) %>%
    group_by(antimalarial_type, antimalarial_label) %>%
    summarise(
      total = sum(point_estimate, na.rm = TRUE),
      total_lower = sum(lower_ci, na.rm = TRUE),
      total_upper = sum(upper_ci, na.rm = TRUE),
      total_sample = sum(sample_size, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    arrange(desc(total))
  
  if (nrow(diagnostic_volume_data) > 0) {
    ggplot(diagnostic_volume_data, aes(x = fct_reorder(antimalarial_label, total), 
                               y = total)) +
      geom_col(fill = "steelblue", alpha = 0.8) +
      geom_errorbar(aes(ymin = total_lower, ymax = total_upper), 
                    width = 0.2, color = "black") +
      coord_flip() +
      labs(
        title = str_wrap("Total Market Volume of Diagnostics by Test Type - National", width = 60),
        x = "Diagnostic Type",
        y = "Total Volume (Tests)",
        caption = "Error bars show 95% confidence intervals"
      ) +
      theme_minimal(base_size = 16) +
      theme(
        plot.title = element_text(face = "bold")
      ) +
      scale_y_continuous(expand = expansion(mult = c(0, 0.15)),
                        labels = scales::comma)
  } else {
    cat("No diagnostic volume data available")
  }
} else {
  cat("No national data available")
}
```

#### Figure: Any Diagnostic Market Volume by Outlet Type (National)

```{r figure_anydiagnostic_outlet_national, fig.width=10, fig.height=6}
if ("national" %in% names(results_list) && nrow(results_list[["national"]]) > 0) {
  
  # Focus on "total" (any diagnostic) volume by outlet type
  anydiagnostic_outlet_data <- results_list[["national"]] %>%
    filter(antimalarial_type == "total") %>%
    arrange(desc(point_estimate))
  
  if (nrow(anydiagnostic_outlet_data) > 0) {
    ggplot(anydiagnostic_outlet_data, aes(x = fct_reorder(outlet_label, point_estimate), 
                                  y = point_estimate)) +
      geom_col(fill = "steelblue", alpha = 0.8) +
      geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), 
                    width = 0.2, color = "black") +
      coord_flip() +
      labs(
        title = str_wrap("Total Any Diagnostic Market Volume by Outlet Type - National", width = 60),
        x = "Outlet Type",
        y = "Total Volume (Tests)",
        caption = "Error bars show 95% confidence intervals"
      ) +
      theme_minimal(base_size = 16) +
      theme(
        plot.title = element_text(face = "bold")
      ) +
      scale_y_continuous(expand = expansion(mult = c(0, 0.15)),
                        labels = scales::comma)
  } else {
    cat("No 'Any Diagnostic' volume data available for national analysis")
  }
} else {
  cat("No national data available for diagnostic volume analysis")
}
```

#### Figure: Total Diagnostic Volume by Test Type and Strata1

```{r figure_diagnostic_volume_strata1, fig.width=12, fig.height=8}
if ("strata1" %in% names(results_list) && nrow(results_list[["strata1"]]) > 0) {
  
  available_diagnostic_types <- intersect(indicator_config$volume_vars, unique(results_list[["strata1"]]$antimalarial_type))
  
  strata1_diagnostic_volume <- results_list[["strata1"]] %>%
    filter(antimalarial_type %in% available_diagnostic_types) %>%
    group_by(antimalarial_type, antimalarial_label, strata1) %>%
    summarise(
      total = sum(point_estimate, na.rm = TRUE),
      total_lower = sum(lower_ci, na.rm = TRUE),
      total_upper = sum(upper_ci, na.rm = TRUE),
      .groups = "drop"
    )
  
  if (nrow(strata1_diagnostic_volume) > 0) {
    ggplot(strata1_diagnostic_volume, aes(x = fct_reorder(antimalarial_label, total), 
                                  y = total, fill = strata1)) +
      geom_col(position = "dodge", alpha = 0.8) +
      geom_errorbar(aes(ymin = total_lower, ymax = total_upper), 
                    position = position_dodge(width = 0.9), width = 0.2) +
      coord_flip() +
      labs(
        title = str_wrap("Total Diagnostic Market Volume by Test Type and Strata1", width = 60),
        x = "Diagnostic Type",
        y = "Total Volume (Tests)",
        fill = "Strata1",
        caption = "Error bars show 95% confidence intervals"
      ) +
      theme_minimal(base_size = 16) +
      theme(
        plot.title = element_text(size = rel(1.1), face = "bold"),
        axis.text = element_text(size = rel(0.9)),
        axis.title = element_text(size = rel(1.0)),
        legend.position = "bottom") +
      scale_fill_brewer(type = "qual", palette = "Set1") +
      scale_y_continuous(expand = expansion(mult = c(0, 0.15)),
                        labels = scales::comma)
  }
}
```

#### Figure: Any Diagnostic Market Volume by Outlet Type and Strata1

```{r figure_anydiagnostic_outlet_strata1, fig.width=12, fig.height=8}
if ("strata1" %in% names(results_list) && nrow(results_list[["strata1"]]) > 0) {
  
  strata1_anydiagnostic <- results_list[["strata1"]] %>%
    filter(antimalarial_type == "total")
  
  if (nrow(strata1_anydiagnostic) > 0) {
    ggplot(strata1_anydiagnostic, aes(x = fct_reorder(outlet_label, point_estimate), 
                              y = point_estimate, fill = strata1)) +
      geom_col(position = "dodge", alpha = 0.8) +
      geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), 
                    position = position_dodge(width = 0.9), width = 0.2) +
      coord_flip() +
      labs(
        title = str_wrap("Total Any Diagnostic Market Volume by Outlet Type and Strata1", width = 60),
        x = "Outlet Type",
        y = "Total Volume (Tests)",
        fill = "Strata1",
        caption = "Error bars show 95% confidence intervals"
      ) +
      theme_minimal(base_size = 16) +
      theme(
        plot.title = element_text(size = rel(1.1), face = "bold"),
        axis.text = element_text(size = rel(0.9)),
        axis.title = element_text(size = rel(1.0)),
        legend.position = "bottom") +
      scale_fill_brewer(type = "qual", palette = "Set1") +
      scale_y_continuous(expand = expansion(mult = c(0, 0.15)),
                        labels = scales::comma)
  }
}
```

`r if(has_strata2) "#### Figure: Total Diagnostic Volume by Test Type and Strata2"`

```{r figure_diagnostic_volume_strata2, fig.width=12, fig.height=8}
if ("strata2" %in% names(results_list) && nrow(results_list[["strata2"]]) > 0) {
  
  available_diagnostic_types <- intersect(indicator_config$volume_vars, unique(results_list[["strata2"]]$antimalarial_type))
  
  strata2_diagnostic_volume <- results_list[["strata2"]] %>%
    filter(antimalarial_type %in% available_diagnostic_types) %>%
    group_by(antimalarial_type, antimalarial_label, strata2) %>%
    summarise(
      total = sum(point_estimate, na.rm = TRUE),
      total_lower = sum(lower_ci, na.rm = TRUE),
      total_upper = sum(upper_ci, na.rm = TRUE),
      .groups = "drop"
    )
  
  if (nrow(strata2_diagnostic_volume) > 0) {
    ggplot(strata2_diagnostic_volume, aes(x = fct_reorder(antimalarial_label, total), 
                                  y = total, fill = strata2)) +
      geom_col(position = "dodge", alpha = 0.8) +
      geom_errorbar(aes(ymin = total_lower, ymax = total_upper), 
                    position = position_dodge(width = 0.9), width = 0.2) +
      coord_flip() +
      labs(
        title = str_wrap("Total Diagnostic Market Volume by Test Type and Strata2", width = 60),
        x = "Diagnostic Type",
        y = "Total Volume (Tests)",
        fill = "Strata2",
        caption = "Error bars show 95% confidence intervals"
      ) +
      theme_minimal(base_size = 16) +
      theme(
        plot.title = element_text(size = rel(1.1), face = "bold"),
        axis.text = element_text(size = rel(0.9)),
        axis.title = element_text(size = rel(1.0)),
        legend.position = "bottom") +
      scale_fill_brewer(type = "qual", palette = "Set2") +
      scale_y_continuous(expand = expansion(mult = c(0, 0.15)),
                        labels = scales::comma)
  }
}
```

`r if(has_strata2) "#### Figure: Any Diagnostic Market Volume by Outlet Type and Strata2"`

```{r figure_anydiagnostic_outlet_strata2, fig.width=12, fig.height=8}
if ("strata2" %in% names(results_list) && nrow(results_list[["strata2"]]) > 0) {
  
  strata2_anydiagnostic <- results_list[["strata2"]] %>%
    filter(antimalarial_type == "total")
  
  if (nrow(strata2_anydiagnostic) > 0) {
    ggplot(strata2_anydiagnostic, aes(x = fct_reorder(outlet_label, point_estimate), 
                              y = point_estimate, fill = strata2)) +
      geom_col(position = "dodge", alpha = 0.8) +
      geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), 
                    position = position_dodge(width = 0.9), width = 0.2) +
      coord_flip() +
      labs(
        title = str_wrap("Total Any Diagnostic Market Volume by Outlet Type and Strata2", width = 60),
        x = "Outlet Type",
        y = "Total Volume (Tests)",
        fill = "Strata2",
        caption = "Error bars show 95% confidence intervals"
      ) +
      theme_minimal(base_size = 16) +
      theme(
        plot.title = element_text(size = rel(1.1), face = "bold"),
        axis.text = element_text(size = rel(0.9)),
        axis.title = element_text(size = rel(1.0)),
        legend.position = "bottom") +
      scale_fill_brewer(type = "qual", palette = "Set2") +
      scale_y_continuous(expand = expansion(mult = c(0, 0.15)),
                        labels = scales::comma)
  }
}
```

`r if(cross_strata_possible) "#### Figure: Any Diagnostic Market Volume by Outlet Type - Cross-Stratification"`

```{r figure_anydiagnostic_cross_strata, fig.width=14, fig.height=10}
if (cross_strata_possible) {
  cross_results <- names(results_list)[grepl("^cross_", names(results_list))]
  
  if (length(cross_results) > 0) {
    # Combine all cross-stratification results for plotting
    all_cross_data <- tibble()
    
    for (cross_name in cross_results) {
      cross_data <- results_list[[cross_name]] %>%
        filter(antimalarial_type == "total") %>%
        mutate(strata1_group = gsub("cross_", "", cross_name))
      all_cross_data <- bind_rows(all_cross_data, cross_data)
    }
    
    if (nrow(all_cross_data) > 0) {
      ggplot(all_cross_data, aes(x = fct_reorder(outlet_label, point_estimate), 
                                y = point_estimate, fill = strata2)) +
        geom_col(position = "dodge", alpha = 0.8) +
        geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), 
                      position = position_dodge(width = 0.9), width = 0.2) +
        facet_wrap(~strata1_group, scales = "fixed") +
        coord_flip() +
        labs(
          title = str_wrap("Total Any Diagnostic Market Volume by Outlet Type - Cross-Stratification", width = 60),
          x = "Outlet Type",
          y = "Total Volume (Tests)",
          fill = "Strata2",
          caption = "Error bars show 95% confidence intervals"
        ) +
        theme_minimal(base_size = 14) +
        theme(
          plot.title = element_text(face = "bold"),
          legend.position = "bottom",
          strip.text = element_text(face = "bold")
        ) +
        scale_fill_brewer(type = "qual", palette = "Set1") +
        scale_y_continuous(expand = expansion(mult = c(0, 0.15)),
                          labels = scales::comma)
    }
  }
}
```

\newpage


## Tables

### Table 1: National Level Results - Volume by Diagnostic × Outlet Matrix

```{r table_national_volume, results='asis'}
if ("national" %in% names(results_list) && nrow(results_list[["national"]]) > 0) {
  
  # Create comprehensive table with total volumes as values
  volume_matrix <- results_list[["national"]] %>%
    select(antimalarial_label, outlet_label, point_estimate) %>%
    pivot_wider(names_from = outlet_label, values_from = point_estimate, values_fill = 0) %>%
    mutate(across(where(is.numeric), ~round(., 0)))
  
  table_output <- knitr::kable(volume_matrix, format = "markdown", 
                              format.args = list(big.mark = ","),
                              caption = "Total Market Volume (AETDs)")
  cat(table_output, sep = "\n")
  cat("\n*", footnotes_list[["national"]], "*\n\n")
  
} else {
  cat("**No national level data available**\n\n")
}
```

\newpag

## Technical Notes

**Survey Design:** Complex sampling with market share weights (`wt_marketShare`), cluster sampling (c4), stratification (strata1), and finite population correction (fpc).

**Population Filter:** Analysis limited to non-booster samples (`booster == 0`).

**Data Source:** Product-level data (_rdt_micro_data_final.csv) in long format - RDT/diagnostic dataset, same as Indicator 3.3.

**Statistical Method:** Survey-weighted total volumes with 95% confidence intervals calculated using `svytotal()` from the survey package.

**Volume Measurement:** Number of blood tests sold per outlet, aggregated to population-level estimates.

**Product Coding:** Products with zero volume are recoded to missing for analysis (following Stata logic: `recode product (0 = .)`). This ensures zero volume products do not affect totals.

**Diagnostic Products:** Uses diagnostic test variables including total (any blood test), microscopy, and RDTs, matching the structure of Indicator 3.3.

**Results Structure:**  
- **National:** Overall results across all geographic reach  
- **Strata1:** Results by primary stratification variable (if present and has variation)  
- **Strata2:** Results by secondary stratification variable (if present and has variation)  
- **Cross-stratification:** Results by strata2 within each level of strata1 (if both strata present)  

**Stratification:** Flexible stratification structure that adapts to available strata variables:  
- **strata1**: Primary stratification variable (may be region, province, urban/rural, etc.)  
- **strata2**: Secondary stratification variable (if present)  
- The script automatically detects and analyzes whatever strata variables exist in your data  

**Excel Output:** Results exported using the standard `create_excel_output()` function with:  
- Separate sheets for each analysis level  
- Antimalarials in rows, outlets in columns  
- Three metrics per outlet: Point (total volume), Lower CI, Upper CI  
- Footnotes with product counts by outlet type  
- Long format sheet for easy analysis  

**Column Structure:** Results use common structure where:  
- `point_estimate` = total volume (AETDs)  
- `lower_ci` = lower bound of 95% CI (set to 0 if negative)  
- `upper_ci` = upper bound of 95% CI  
- `sample_size` = number of products included in calculation  

---

**Report generated:** `r format(Sys.time(), '%B %d, %Y at %I:%M %p')`
