---
title: "ACTwatch Indicator 6.1b - Purchase Price of Antimalarial AETDs (Tablets, Local Currency)"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output: 
  word_document:
    toc: false
    toc_depth: 2
    reference_docx: null
---

## Indicator Definition

**Indicator Group:** Price - Purchase price of antimalarials from suppliers

**Description:** The median purchase price per Adult Equivalent Treatment Dose (AETD) of antimalarial tablet formulations from suppliers, measured in local currency, by antimalarial type and outlet type

**Numerator:** Median purchase price per AETD (local currency) for a specific antimalarial product/category

**Denominator:** All tablet formulation products with purchase price data available for that product/category

**Disaggregation:** By antimalarial type and outlet type; additional disaggregation by strata if available

**Data Source:** Product data (long format) - tablet formulations only

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                      fig.width = 12, fig.height = 8)

library(tidyverse)
library(survey)
library(openxlsx)
library(forcats)
library(here)
library(data.table)

# Set parameters
if (!exists("country")) stop("Global variable 'country' not found")
if (!exists("year")) stop("Global variable 'year' not found") 

# Configuration matching the Stata analysis structure
indicator_config <- list(
  indicator_id = "6.1b",
  title = "Purchase Price of Antimalarial AETDs (Tablets, Local Currency)", 
  description = "Median purchase price per AETD of antimalarial tablet formulations by type and outlet",
  
  # Analysis settings
  dataset = "product", # Product data in long format
  analysis_type = "price",
  survey_weight = "wt_alloutlet", # Standard outlet weight for price analysis
  price_variable = "suppriceperaetd", # Purchase price per AETD in local currency
  population_filter = quote(booster == 0 & a3 == 1 & countprod == 1), # Tablets only, non-booster, counted products
  
  # Outlet types (matching Stata outvars1)
  outlet_dummies = c("private_nonprofit", "private_forprofit", "pharmacy",
                    "laboratory", "drug_store", "total_informal", "wholesale"),
  outlet_labels = list(
    "private_nonprofit" = "Private Not-for-Profit",
    "private_forprofit" = "Private For-Profit", 
    "pharmacy" = "Pharmacy",
    "laboratory" = "Laboratory", 
    "drug_store" = "Drug Store",
    "total_informal" = "Informal (Total)",
    "wholesale" = "Wholesaler"
  ),

  # Antimalarial products for price analysis (matching Stata pri_cov - same as volume_vars)
  price_vars = c(
    "anyam",              # Any antimalarial
    "anyact",             # Any ACT
    "al",                 # Artemether lumefantrine
    "asaq",               # Artesunate amodiaquine
    "appq",               # Artemisinin piperaquine
    "dhappq",             # Dihydroartemisinin piperaquine
    "arppq",              # Arterolane piperaquine
    "otheract",           # Any other ACT
    "qaact",              # QA ACT
    "qa_all",             # WHO PQ and nationally approved
    "qa_who",             # WHO PQ but not nationally approved
    "qa_nat",             # Nationally approved but not WHO PQ
    "qa_none",            # Not QA or nationally approved
    "nonart",             # Non-artemisinins
    "oralqn",             # Oral quinine
    "cq",                 # Chloroquine
    "sp",                 # Sulfadoxine pyrimethamine
    "spaq",               # Sulfadoxine pyrimethamine amodiaquine
    "nonartoth",          # Other non-artemisinins
    "oartmono",           # Oral artemisinin monotherapy
    "noartmono",          # Non-oral artemisinin monotherapy
    "severe",             # Treatment for severe malaria
    "recas",              # Rectal artesunate
    "injas",              # Injectable artesunate
    "injar",              # Injectable artemether
    "injae",              # Injectable arteether
    "injqn"               # Injectable quinine
  ),
  
  # Product labels for better display
  price_labels = list(
    "anyam" = "Any antimalarial",
    "anyact" = "Any ACT",
    "al" = "Artemether-lumefantrine",
    "asaq" = "Artesunate-amodiaquine", 
    "appq" = "Artemisinin-piperaquine",
    "dhappq" = "Dihydroartemisinin-piperaquine",
    "arppq" = "Arterolane-piperaquine",
    "otheract" = "Any other ACT",
    "qaact" = "QA ACT",
    "qa_all" = "ACT that is both WHO PQ and nationally approved",
    "qa_who" = "ACT that is WHO PQ but not nationally approved", 
    "qa_nat" = "ACT that is nationally approved but not WHO PQ",
    "qa_none" = "ACT not QA or nationally approved",
    "nonart" = "Non-artemisinins", 
    "oralqn" = "Oral quinine",
    "cq" = "Chloroquine",
    "sp" = "Sulfadoxine-pyrimethamine",
    "spaq" = "Sulfadoxine pyrimethamine amodiaquine",
    "nonartoth" = "Other non-artemisinins",
    "oartmono" = "Oral artemisinin monotherapy",
    "noartmono" = "Non-oral artemisinin monotherapy",
    "severe" = "Treatment for severe malaria",
    "recas" = "Rectal artesunate",
    "injas" = "Injectable artesunate",
    "injar" = "Injectable artemether",
    "injae" = "Injectable arteether", 
    "injqn" = "Injectable quinine"
  ),
  
  # ACT types for focused analysis
  act_types = c("anyact", "al", "asaq", "appq", "dhappq", "arppq", "otheract"),
  
  # Output settings
  file_suffix = "Purchase price of AETDs from suppliers"
)

# Source the create_excel_function (if available)
excel_function_path <- here("Scripts", "3_Analysis", "create_excel_function.R")
if (file.exists(excel_function_path)) {
  source(excel_function_path)
}
```

```{r load_data, include=FALSE}
# Load product data (long format)
data_file <- here("Data", "Final data", 
                  paste0(country, "_", year, "_full_data.csv"))

if (!file.exists(data_file)) {
  stop("Data file not found: ", data_file)
}

product_data <- fread(data_file) %>%
  # Ensure strata variables are character
  mutate(across(any_of(c("strata1", "strata2")), as.character)) %>%
  # Clean up blank but non-missing strata values
  mutate(
    strata1 = dplyr::na_if(strata1, ""),
    strata2 = dplyr::na_if(strata2, "")
  ) %>%
  # Drop if outlet category information is missing (following Stata logic)
  filter(!is.na(outcat2))

# Check for price variable
if (!indicator_config$price_variable %in% names(product_data)) {
  stop("Price variable '", indicator_config$price_variable, "' not found in data")
}
```

```{r data_processing, include=FALSE}
# Following Stata logic: ensure outlet variables are coded as 0/1
available_outlet_vars <- intersect(indicator_config$outlet_dummies, names(product_data))

# Create data for footnotes (has population filter but NOT missing price filter)
footnote_data <- product_data %>%
  # Recode outlet variables (following Stata: recode `x'(.=0) if countprod==1)
  mutate(
    across(all_of(available_outlet_vars), 
           ~ifelse(is.na(.) & countprod == 1, 0, .))
  ) %>%
  # Apply population filter (tablets only, non-booster, counted products)
  filter(!!indicator_config$population_filter)

# Create processed data WITH missing price filter for analysis
processed_data <- footnote_data %>%
  filter(!is.na(!!sym(indicator_config$price_variable)))

# Detect strata structure
strata_info <- list()
if ("strata1" %in% names(processed_data) && 
    length(unique(na.omit(processed_data$strata1))) > 1) {
  strata1_values <- unique(na.omit(processed_data$strata1))
  strata1_values <- strata1_values[strata1_values != "" & !is.na(trimws(strata1_values))]
  if (length(strata1_values) > 1) {
    strata_info$strata1 <- list(variable = "strata1", values = strata1_values)
  }
}

if ("strata2" %in% names(processed_data) && 
    length(unique(na.omit(processed_data$strata2))) > 1) {
  strata2_values <- unique(na.omit(processed_data$strata2))
  strata2_values <- strata2_values[strata2_values != "" & !is.na(trimws(strata2_values))]
  if (length(strata2_values) > 1) {
    strata_info$strata2 <- list(variable = "strata2", values = strata2_values)
  }
}

has_strata1 <- "strata1" %in% names(strata_info)
has_strata2 <- "strata2" %in% names(strata_info)
cross_strata_possible <- has_strata1 && has_strata2
```

```{r survey_setup, include=FALSE}
# Setup survey design (following Stata: svyset c4 [pweight=wt_allOutlet], strata(strata) fpc(fpc))
survey_design <- processed_data %>%
  filter(!is.na(!!sym(indicator_config$survey_weight))) %>%
  as_survey_design(
    ids = c4,
    weights = !!sym(indicator_config$survey_weight),
    strata = strata1,  # Using strata1 as primary design strata
    fpc = fpc
  )
```

```{r analysis_functions, include=FALSE}
# Calculate median prices using weighted percentiles (standardized output format)
calculate_price_medians <- function(survey_data, group_vars = NULL) {
  
  results <- tibble()
  
  # Available price variables (antimalarial products) in the dataset
  available_price_vars <- intersect(indicator_config$price_vars, 
                                    names(survey_data$variables))
  
  # Available outlet variables in the dataset  
  available_outlet_vars <- intersect(indicator_config$outlet_dummies, 
                                    names(survey_data$variables))
  
  price_var_name <- indicator_config$price_variable
  
  for (antimalarial_var in available_price_vars) {
    for (outlet_var in available_outlet_vars) {
      
      tryCatch({
        if (is.null(group_vars)) {
          # National analysis
          outlet_data_raw <- survey_data$variables %>%
            filter(!!sym(outlet_var) == 1, 
                   !!sym(antimalarial_var) == 1,
                   !is.na(!!sym(price_var_name)))
          
          if (nrow(outlet_data_raw) > 5) {  # Sufficient observations
            # Use weighted percentiles directly on the raw data
            if (requireNamespace("statar", quietly = TRUE)) {
              percentiles <- statar::pctile(
                outlet_data_raw[[price_var_name]], 
                probs = c(0.25, 0.50, 0.75),
                wt = outlet_data_raw[[indicator_config$survey_weight]]
              )
              
              result_row <- tibble(
                antimalarial_type = antimalarial_var,
                outlet_type = outlet_var,
                point_estimate = percentiles[2],  # Median price
                lower_ci = percentiles[1],        # Q25
                upper_ci = percentiles[3],        # Q75
                sample_size = nrow(outlet_data_raw),
                antimalarial_label = indicator_config$price_labels[[antimalarial_var]] %||% antimalarial_var,
                outlet_label = indicator_config$outlet_labels[[outlet_var]] %||% outlet_var
              )
              
              results <- bind_rows(results, result_row)
            } else {
              # Fallback to survey package if statar not available
              subset_design <- subset(survey_data, 
                                     !!sym(outlet_var) == 1 & 
                                     !!sym(antimalarial_var) == 1 &
                                     !is.na(!!sym(price_var_name)))
              
              price_formula <- as.formula(paste0("~", price_var_name))
              q25 <- svyquantile(price_formula, subset_design, quantiles = 0.25, method = "constant")
              q50 <- svyquantile(price_formula, subset_design, quantiles = 0.50, method = "constant") 
              q75 <- svyquantile(price_formula, subset_design, quantiles = 0.75, method = "constant")
              
              result_row <- tibble(
                antimalarial_type = antimalarial_var,
                outlet_type = outlet_var,
                point_estimate = as.numeric(q50),  # Median price
                lower_ci = as.numeric(q25),        # Q25
                upper_ci = as.numeric(q75),        # Q75
                sample_size = nrow(outlet_data_raw),
                antimalarial_label = indicator_config$price_labels[[antimalarial_var]] %||% antimalarial_var,
                outlet_label = indicator_config$outlet_labels[[outlet_var]] %||% outlet_var
              )
              
              results <- bind_rows(results, result_row)
            }
          }
          
        } else {
          # Strata analysis
          strata_values <- unique(survey_data$variables[[group_vars[1]]])
          strata_values <- strata_values[!is.na(strata_values)]
          
          for (strata_val in strata_values) {
            outlet_data_raw <- survey_data$variables %>%
              filter(!!sym(group_vars[1]) == strata_val,
                     !!sym(outlet_var) == 1, 
                     !!sym(antimalarial_var) == 1,
                     !is.na(!!sym(price_var_name)))
            
            if (nrow(outlet_data_raw) > 5) {
              if (requireNamespace("statar", quietly = TRUE)) {
                percentiles <- statar::pctile(
                  outlet_data_raw[[price_var_name]], 
                  probs = c(0.25, 0.50, 0.75),
                  wt = outlet_data_raw[[indicator_config$survey_weight]]
                )
                
                result_row <- tibble(
                  antimalarial_type = antimalarial_var,
                  outlet_type = outlet_var,
                  point_estimate = percentiles[2],  # Median price
                  lower_ci = percentiles[1],        # Q25
                  upper_ci = percentiles[3],        # Q75
                  sample_size = nrow(outlet_data_raw),
                  antimalarial_label = indicator_config$price_labels[[antimalarial_var]] %||% antimalarial_var,
                  outlet_label = indicator_config$outlet_labels[[outlet_var]] %||% outlet_var
                )
                
                result_row[[group_vars[1]]] <- as.character(strata_val)
                results <- bind_rows(results, result_row)
              } else {
                # Fallback to survey package
                subset_design <- subset(survey_data, 
                                       !!sym(group_vars[1]) == strata_val &
                                       !!sym(outlet_var) == 1 & 
                                       !!sym(antimalarial_var) == 1 &
                                       !is.na(!!sym(price_var_name)))
                
                price_formula <- as.formula(paste0("~", price_var_name))
                q25 <- svyquantile(price_formula, subset_design, quantiles = 0.25, method = "constant")
                q50 <- svyquantile(price_formula, subset_design, quantiles = 0.50, method = "constant")
                q75 <- svyquantile(price_formula, subset_design, quantiles = 0.75, method = "constant")
                
                result_row <- tibble(
                  antimalarial_type = antimalarial_var,
                  outlet_type = outlet_var,
                  point_estimate = as.numeric(q50),  # Median price
                  lower_ci = as.numeric(q25),        # Q25
                  upper_ci = as.numeric(q75),        # Q75
                  sample_size = nrow(outlet_data_raw),
                  antimalarial_label = indicator_config$price_labels[[antimalarial_var]] %||% antimalarial_var,
                  outlet_label = indicator_config$outlet_labels[[outlet_var]] %||% outlet_var
                )
                
                result_row[[group_vars[1]]] <- as.character(strata_val)
                results <- bind_rows(results, result_row)
              }
            }
          }
        }
        
      }, error = function(e) {
        message("Error processing ", antimalarial_var, " in ", outlet_var, ": ", e$message)
      })
    }
  }
  
  return(results)
}

# Calculate footnotes (price data availability and incomplete interviews)
calculate_footnotes <- function(data, strata1_var = NULL) {
  
  # Incomplete interview criteria (same as Stata)
  incomplete_criteria <- c(203,204,205,207,208,303,304,305,307,308,309,310)
  
  price_var_name <- indicator_config$price_variable
  
  if (is.null(strata1_var)) {
    # National counts
    n_total <- sum(data$anyam == 1 & !is.na(data[[price_var_name]]), na.rm = TRUE)
    
    incomplete_count <- sum(data$finalintstat %in% incomplete_criteria & 
                       data$anyam == 1, na.rm = TRUE)
    
    missing_price <- sum(data$anyam == 1 & is.na(data[[price_var_name]]), na.rm = TRUE)
    
    return(paste0("Prices are per AETD of tablet formulations only. ",
                  "Sample size = ", n_total, "; ",
                  "N outlets not completing full interview = ", incomplete_count, "; ",
                  "N products missing price data = ", missing_price))
    
  } else {
    # Strata-specific counts
    strata_levels <- unique(data[[strata1_var]])
    strata_levels <- strata_levels[!is.na(strata_levels)]
    
    # Build sample sizes
    sample_sizes <- c()
    for (strata_val in strata_levels) {
      n <- sum(data[[strata1_var]] == strata_val & 
               data$anyam == 1 & 
               !is.na(data[[price_var_name]]), na.rm = TRUE)
      sample_sizes <- c(sample_sizes, paste0(strata_val, " = ", n))
    }
    
    # Build incomplete interview counts
    incomplete_counts <- c()
    for (strata_val in strata_levels) {
      incomplete <- sum(data[[strata1_var]] == strata_val &
                   data$finalintstat %in% incomplete_criteria & 
                   data$anyam == 1, na.rm = TRUE)
      incomplete_counts <- c(incomplete_counts, paste0(strata_val, " = ", incomplete))
    }
    
    # Build missing price counts
    missing_counts <- c()
    for (strata_val in strata_levels) {
      missing <- sum(data[[strata1_var]] == strata_val &
                    data$anyam == 1 & 
                    is.na(data[[price_var_name]]), na.rm = TRUE)
      missing_counts <- c(missing_counts, paste0(strata_val, " = ", missing))
    }
    
    return(paste0("Prices are per AETD of tablet formulations only. ",
                  "Sample sizes: ", paste(sample_sizes, collapse = "; "), "; ",
                  "N outlets not completing full interview: ", paste(incomplete_counts, collapse = "; "), "; ",
                  "N products missing price data: ", paste(missing_counts, collapse = "; ")))
  }
}
```

```{r run_analysis, include=FALSE}
# Initialize results storage
results_list <- list()
footnotes_list <- list()

# 1. National level results
national_results <- calculate_price_medians(survey_design)
national_footnote <- calculate_footnotes(footnote_data)

results_list[["national"]] <- national_results
footnotes_list[["national"]] <- national_footnote

# 2. Strata1 results (if available)
if (has_strata1) {
  strata1_results <- calculate_price_medians(survey_design, group_vars = "strata1")
  
  if (nrow(strata1_results) > 0) {
    results_list[["strata1"]] <- strata1_results
    strata1_footnotes <- calculate_footnotes(footnote_data, strata1_var = "strata1")
    footnotes_list[["strata1"]] <- strata1_footnotes
  }
}

# 3. Strata2 results (if available)  
if (has_strata2) {
  strata2_results <- calculate_price_medians(survey_design, group_vars = "strata2")
  
  if (nrow(strata2_results) > 0) {
    results_list[["strata2"]] <- strata2_results
    strata2_footnotes <- calculate_footnotes(footnote_data, strata1_var = "strata2")
    footnotes_list[["strata2"]] <- strata2_footnotes
  }
}

# 4. Cross-stratification results (if both strata available)
if (cross_strata_possible) {
  for (strata1_val in strata_info$strata1$values) {
    # Filter to specific strata1 value for both analysis and footnotes
    strata1_subset <- processed_data %>%
      filter(strata1 == strata1_val)
    
    strata1_footnote_subset <- footnote_data %>%
      filter(strata1 == strata1_val)
    
    if (nrow(strata1_subset) > 10) {  # Sufficient data
      # Create survey design for this subset
      strata1_survey <- strata1_subset %>%
        filter(!is.na(!!sym(indicator_config$survey_weight))) %>%
        as_survey_design(
          ids = c4,
          weights = !!sym(indicator_config$survey_weight),
          strata = strata2,
          fpc = fpc
        )
      
      # Calculate prices by strata2 within this strata1 value
      cross_results <- calculate_price_medians(strata1_survey, group_vars = "strata2")
      
      if (nrow(cross_results) > 0) {
        # Add strata1 identifier
        cross_results$strata1 <- strata1_val
        results_list[[paste0("cross_", strata1_val)]] <- cross_results
        
        # Calculate footnotes for this cross-stratification
        cross_footnotes <- calculate_footnotes(strata1_footnote_subset, strata1_var = "strata2")
        footnotes_list[[paste0("cross_", strata1_val)]] <- cross_footnotes
      }
    }
  }
}
```

```{r export_excel, include=FALSE}
# Use the standard create_excel_output function
excel_success <- create_excel_output(
  results_list = results_list,
  footnotes_list = footnotes_list, 
  indicator_config = indicator_config,
  country = country,
  year = year,
  include_antimalarial_col = TRUE
)

if (excel_success) {
  cat("Excel file created successfully\n")
} else {
  cat("Warning: Excel file creation encountered issues\n")
}
```

\newpage

## Figures

### Figure 1: Median ACT Purchase Prices by ACT Type (National)

```{r figure_act_prices, fig.width=12, fig.height=8}
if ("national" %in% names(results_list) && nrow(results_list[["national"]]) > 0) {
  
  available_act_types <- intersect(indicator_config$act_types, 
                                  unique(results_list[["national"]]$antimalarial_type))
  
  national_act_prices <- results_list[["national"]] %>%
    filter(antimalarial_type %in% available_act_types) %>%
    group_by(antimalarial_type, antimalarial_label) %>%
    summarise(
      median_price = weighted.mean(point_estimate, sample_size, na.rm = TRUE),
      q25 = weighted.mean(lower_ci, sample_size, na.rm = TRUE),
      q75 = weighted.mean(upper_ci, sample_size, na.rm = TRUE),
      .groups = "drop"
    )
  
  if (nrow(national_act_prices) > 0) {
    ggplot(national_act_prices, aes(x = fct_reorder(antimalarial_label, median_price), 
                                    y = median_price)) +
      geom_col(fill = "#2171b5", alpha = 0.8) +
      geom_errorbar(aes(ymin = q25, ymax = q75), width = 0.3) +
      coord_flip() +
      labs(
        title = "Median ACT Purchase Prices by ACT Type (National Level)",
        x = "ACT Type",
        y = "Median Purchase Price per AETD (Local Currency)",
        caption = "Error bars show interquartile range (Q25-Q75)"
      ) +
      theme_minimal(base_size = 14) +
      theme(
        plot.title = element_text(face = "bold"),
        axis.text = element_text(size = 12)
      ) +
      scale_y_continuous(expand = expansion(mult = c(0, 0.15)))
  }
}
```

### Figure 2: Median Any ACT Purchase Price by Outlet Type (National)

```{r figure_anyact_outlet, fig.width=12, fig.height=8}
if ("national" %in% names(results_list) && nrow(results_list[["national"]]) > 0) {
  
  national_anyact <- results_list[["national"]] %>%
    filter(antimalarial_type == "anyact")
  
  if (nrow(national_anyact) > 0) {
    ggplot(national_anyact, aes(x = fct_reorder(outlet_label, point_estimate), 
                                y = point_estimate)) +
      geom_col(fill = "#238b45", alpha = 0.8) +
      geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.3) +
      coord_flip() +
      labs(
        title = "Median Any ACT Purchase Price by Outlet Type (National Level)",
        x = "Outlet Type",
        y = "Median Purchase Price per AETD (Local Currency)",
        caption = "Error bars show interquartile range (Q25-Q75)"
      ) +
      theme_minimal(base_size = 14) +
      theme(
        plot.title = element_text(face = "bold"),
        axis.text = element_text(size = 12)
      ) +
      scale_y_continuous(expand = expansion(mult = c(0, 0.15)))
  }
}
```

`r if(has_strata1) "### Figure 3: ACT Purchase Prices by ACT Type and Strata1"`

```{r figure_act_prices_strata1, fig.width=12, fig.height=8}
if ("strata1" %in% names(results_list) && nrow(results_list[["strata1"]]) > 0) {
  
  available_act_types <- intersect(indicator_config$act_types, 
                                  unique(results_list[["strata1"]]$antimalarial_type))
  
  strata1_act_prices <- results_list[["strata1"]] %>%
    filter(antimalarial_type %in% available_act_types) %>%
    group_by(antimalarial_type, antimalarial_label, strata1) %>%
    summarise(
      median_price = weighted.mean(point_estimate, sample_size, na.rm = TRUE),
      q25 = weighted.mean(lower_ci, sample_size, na.rm = TRUE),
      q75 = weighted.mean(upper_ci, sample_size, na.rm = TRUE),
      .groups = "drop"
    )
  
  if (nrow(strata1_act_prices) > 0) {
    ggplot(strata1_act_prices, aes(x = fct_reorder(antimalarial_label, median_price), 
                                   y = median_price, fill = strata1)) +
      geom_col(position = "dodge", alpha = 0.8) +
      geom_errorbar(aes(ymin = q25, ymax = q75), 
                    position = position_dodge(width = 0.9), width = 0.2) +
      coord_flip() +
      labs(
        title = "Median ACT Purchase Prices by ACT Type and Strata1",
        x = "ACT Type",
        y = "Median Purchase Price per AETD (Local Currency)",
        fill = "Strata1",
        caption = "Error bars show interquartile range (Q25-Q75)"
      ) +
      theme_minimal(base_size = 14) +
      theme(
        plot.title = element_text(face = "bold"),
        legend.position = "bottom"
      ) +
      scale_fill_brewer(type = "qual", palette = "Set1") +
      scale_y_continuous(expand = expansion(mult = c(0, 0.15)))
  }
}
```

`r if(has_strata2) "### Figure 4: ACT Purchase Prices by ACT Type and Strata2"`

```{r figure_act_prices_strata2, fig.width=12, fig.height=8}
if ("strata2" %in% names(results_list) && nrow(results_list[["strata2"]]) > 0) {
  
  available_act_types <- intersect(indicator_config$act_types, 
                                  unique(results_list[["strata2"]]$antimalarial_type))
  
  strata2_act_prices <- results_list[["strata2"]] %>%
    filter(antimalarial_type %in% available_act_types) %>%
    group_by(antimalarial_type, antimalarial_label, strata2) %>%
    summarise(
      median_price = weighted.mean(point_estimate, sample_size, na.rm = TRUE),
      q25 = weighted.mean(lower_ci, sample_size, na.rm = TRUE),
      q75 = weighted.mean(upper_ci, sample_size, na.rm = TRUE),
      .groups = "drop"
    )
  
  if (nrow(strata2_act_prices) > 0) {
    ggplot(strata2_act_prices, aes(x = fct_reorder(antimalarial_label, median_price), 
                                   y = median_price, fill = strata2)) +
      geom_col(position = "dodge", alpha = 0.8) +
      geom_errorbar(aes(ymin = q25, ymax = q75), 
                    position = position_dodge(width = 0.9), width = 0.2) +
      coord_flip() +
      labs(
        title = "Median ACT Purchase Prices by ACT Type and Strata2",
        x = "ACT Type",
        y = "Median Purchase Price per AETD (Local Currency)",
        fill = "Strata2",
        caption = "Error bars show interquartile range (Q25-Q75)"
      ) +
      theme_minimal(base_size = 14) +
      theme(
        plot.title = element_text(face = "bold"),
        legend.position = "bottom"
      ) +
      scale_fill_brewer(type = "qual", palette = "Set2") +
      scale_y_continuous(expand = expansion(mult = c(0, 0.15)))
  }
}
```

`r if(has_strata2) "### Figure 5: Any ACT Purchase Price by Outlet Type and Strata2"`

```{r figure_anyact_outlet_strata2, fig.width=12, fig.height=8}
if ("strata2" %in% names(results_list) && nrow(results_list[["strata2"]]) > 0) {
  
  strata2_anyact <- results_list[["strata2"]] %>%
    filter(antimalarial_type == "anyact")
  
  if (nrow(strata2_anyact) > 0) {
    ggplot(strata2_anyact, aes(x = fct_reorder(outlet_label, point_estimate), 
                               y = point_estimate, fill = strata2)) +
      geom_col(position = "dodge", alpha = 0.8) +
      geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), 
                    position = position_dodge(width = 0.9), width = 0.2) +
      coord_flip() +
      labs(
        title = "Median Any ACT Purchase Price by Outlet Type and Strata2",
        x = "Outlet Type",
        y = "Median Purchase Price per AETD (Local Currency)",
        fill = "Strata2",
        caption = "Error bars show interquartile range (Q25-Q75)"
      ) +
      theme_minimal(base_size = 14) +
      theme(
        plot.title = element_text(face = "bold"),
        legend.position = "bottom"
      ) +
      scale_fill_brewer(type = "qual", palette = "Set2") +
      scale_y_continuous(expand = expansion(mult = c(0, 0.15)))
  }
}
```

`r if(cross_strata_possible) "### Figure 6: Any ACT Purchase Price by Outlet Type - Cross-Stratification"`

```{r figure_anyact_cross_strata, fig.width=14, fig.height=10}
if (cross_strata_possible) {
  cross_results <- names(results_list)[grepl("^cross_", names(results_list))]
  
  if (length(cross_results) > 0) {
    # Combine all cross-stratification results for plotting
    all_cross_data <- tibble()
    
    for (cross_name in cross_results) {
      cross_data <- results_list[[cross_name]] %>%
        filter(antimalarial_type == "anyact") %>%
        mutate(strata1_group = gsub("cross_", "", cross_name))
      all_cross_data <- bind_rows(all_cross_data, cross_data)
    }
    
    if (nrow(all_cross_data) > 0) {
      ggplot(all_cross_data, aes(x = fct_reorder(outlet_label, point_estimate), 
                                y = point_estimate, fill = strata2)) +
        geom_col(position = "dodge", alpha = 0.8) +
        geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), 
                      position = position_dodge(width = 0.9), width = 0.2) +
        facet_wrap(~strata1_group, scales = "fixed") +
        coord_flip() +
        labs(
          title = "Median Any ACT Purchase Price by Outlet Type - Cross-Stratification",
          x = "Outlet Type",
          y = "Median Purchase Price per AETD (Local Currency)",
          fill = "Strata2",
          caption = "Error bars show interquartile range (Q25-Q75)"
        ) +
        theme_minimal(base_size = 14) +
        theme(
          plot.title = element_text(face = "bold"),
          legend.position = "bottom",
          strip.text = element_text(face = "bold")
        ) +
        scale_fill_brewer(type = "qual", palette = "Set1") +
        scale_y_continuous(expand = expansion(mult = c(0, 0.15)))
    }
  }
}
```

\newpage

## Tables

### Table 1: National Level Results - Purchase Price by Antimalarial × Outlet Matrix

```{r table_national_price, results='asis'}
if ("national" %in% names(results_list) && nrow(results_list[["national"]]) > 0) {
  
  # Create comprehensive table with median prices as values
  price_matrix <- results_list[["national"]] %>%
    select(antimalarial_label, outlet_label, point_estimate) %>%
    pivot_wider(names_from = outlet_label, values_from = point_estimate, values_fill = NA) %>%
    mutate(across(where(is.numeric), ~round(., 2)))
  
  table_output <- knitr::kable(price_matrix, format = "markdown",
                              caption = "Median Purchase Price per AETD (Local Currency)")
  cat(table_output, sep = "\n")
  cat("\n*", footnotes_list[["national"]], "*\n\n")
  
} else {
  cat("**No national level data available**\n\n")
}
```

\newpage

## Technical Notes

**Survey Design:** Complex sampling with outlet weights (`wt_alloutlet`), cluster sampling (c4), stratification (strata1), and finite population correction (fpc).

**Population Filter:** Analysis limited to:  
- Tablet formulations only (`a3 == 1`)  
- Non-booster samples (`booster == 0`)  
- Counted products (`countprod == 1`)  
- Products with non-missing purchase price data  

**Price Variable:** `suppriceperaetd` - Purchase price per Adult Equivalent Treatment Dose from suppliers in local currency

**Statistical Method:** Survey-weighted quantiles (25th, 50th, and 75th percentiles) using `statar::pctile()` for weighted percentiles, with fallback to `survey` package's `svyquantile()`.

**Antimalarial Products:** Uses the same comprehensive list as Indicators 3.1, 4.1, and 5.1a, including ACTs, non-artemisinin antimalarials, and treatments for severe malaria.

**Results Structure:**  
- **National:** Overall purchase price medians across all outlets  
- **Strata1:** Purchase price medians by primary stratification variable (if present and varies)  
- **Strata2:** Purchase price medians by secondary stratification variable (if present and varies)  
- **Cross-stratification:** Purchase price medians by strata2 within each level of strata1 (if both strata present)  

**Flexible Stratification:** Uses generic `strata1` and `strata2` variable names that automatically adapt to whatever stratification structure exists in your data.

**Excel Output:** Results exported to Excel workbook using common function with standardized column structure. Median prices appear as "Point Estimate" and quartiles as "Lower CI"/"Upper CI".

**Data Standardization:** Results use common column structure where:  
- `point_estimate` = median purchase price per AETD (local currency)  
- `lower_ci` = 25th percentile (Q25)  
- `upper_ci` = 75th percentile (Q75)  

---

**Report generated:** `r format(Sys.time(), '%B %d, %Y at %I:%M %p')`
