---
title: "ACTwatch Indicator 2.3 - Availability of Malaria Tests in All Screened Outlets"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output: 
  word_document:
    toc: false
    toc_depth: 2
    reference_docx: null
---

## Indicator Definition

**Indicator Group:** Availability among all screened outlets

**Description:** The proportion of all screened outlets with malaria diagnostic tests in stock on the day of the survey visit, disaggregated by test type and outlet type

**Numerator:** Number of screened outlets with a specific test type in stock

**Denominator:** Total number of screened outlets of a given type

**Disaggregation:** By test type and outlet type; additional disaggregation by strata if available

**Data Source:** Outlet data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                      fig.width = 12, fig.height = 8)

library(tidyverse)
library(survey)
library(openxlsx)
library(forcats)
library(here)
library(data.table)


# Set parameters
if (!exists("country")) stop("Global variable 'country' not found")
if (!exists("year")) stop("Global variable 'year' not found") 

# Configuration matching the Stata analysis structure
indicator_config <- list(
  indicator_id = "2.3",
  title = "Availability of Malaria Tests in All Screened Outlets",
  description = "Proportion of screened outlets with malaria diagnostic tests in stock by type",
  
  # Analysis settings
  dataset = "outlet",
  analysis_type = "availability",
  survey_weight = "wt_alloutlet",
  population_filter = quote(screened == 1),
  
  # Outlet types (matching Stata .do file abbreviations)
  outlet_dummies = c("private_nonprofit", "private_forprofit", "pharmacy",
                    "laboratory", "drug_store", "total_informal", "total_retail", "wholesale"),
  outlet_labels = list(
    "private_nonprofit" = "Private Not-for-Profit",
    "private_forprofit" = "Private For-Profit", 
    "pharmacy" = "Pharmacy",
    "laboratory" = "Laboratory",
    "drug_store" = "Drug Store",
    "total_informal" = "Informal (Total)",
    "total_retail" = "Retail (Total)",
    "wholesale" = "Wholesaler"
  ),

  # Test variables (matching local definitions file)
  test_vars = c(
    "st_test",      # Any malaria test
    "st_rdt",       # Any RDT
    "st_micro",     # Microscopy
    "st_qardt"      # Quality assured RDT
  ),
  
  # Test labels for display
  test_labels = list(
    "st_test" = "Any malaria test",
    "st_rdt" = "Any RDT",
    "st_micro" = "Microscopy",
    "st_qardt" = "Quality assured RDT"
  ),
  
  test_order = c("Any malaria test", "Any RDT", "Microscopy", "Quality assured RDT"),
  
  # Alias for Excel function compatibility
  antimalarial_order = c("Any malaria test", "Any RDT", "Microscopy", "Quality assured RDT"),
  
  # Test types for focused figures
  test_types_fig = c("st_rdt", "st_micro", "st_qardt"),
  
  # Output settings
  file_suffix = "Availability of tests in all screened outlets"
)
```

```{r load_data, include=FALSE}
# Load outlet data
data_file <- here("Data", "Final data", 
                  paste0(country, "_", year, "_outlet_data.csv"))

if (!file.exists(data_file)) {
  stop("Data file not found: ", data_file)
}

outlet_data <- fread(data_file) %>%
  mutate(across(any_of(c("strata1", "strata2")), as.character)) %>%
  mutate(
    strata1 = dplyr::na_if(strata1, ""),
    strata2 = dplyr::na_if(strata2, "")
  )
```

```{r data_processing, include=FALSE}
# Apply population filter (screened outlets only)
processed_data <- outlet_data %>%
  filter(!!indicator_config$population_filter)

# Detect strata structure
strata_info <- list()
if ("strata1" %in% names(processed_data) && 
    length(unique(na.omit(processed_data$strata1))) > 1) {
  strata1_values <- unique(na.omit(processed_data$strata1))
  strata1_values <- strata1_values[strata1_values != "" & !is.na(trimws(strata1_values))]
  if (length(strata1_values) > 1) {
    strata_info$strata1 <- list(variable = "strata1", values = strata1_values)
  }
}

if ("strata2" %in% names(processed_data) && 
    length(unique(na.omit(processed_data$strata2))) > 1) {
  strata2_values <- unique(na.omit(processed_data$strata2))
  strata2_values <- strata2_values[strata2_values != "" & !is.na(trimws(strata2_values))]
  if (length(strata2_values) > 1) {
    strata_info$strata2 <- list(variable = "strata2", values = strata2_values)
  }
}

has_strata1 <- "strata1" %in% names(strata_info)
has_strata2 <- "strata2" %in% names(strata_info)
cross_strata_possible <- has_strata1 && has_strata2
```

```{r survey_setup, include=FALSE}
# Setup survey design
survey_design <- processed_data %>%
  filter(!is.na(!!sym(indicator_config$survey_weight))) %>%
  as_survey_design(
    ids = c4,
    weights = !!sym(indicator_config$survey_weight),
    strata = strata1,
    fpc = fpc
  )
```

```{r analysis_functions, include=FALSE}
# Calculate availability (proportion of outlets with test in stock)
calculate_availability <- function(survey_data, group_vars = NULL) {
  
  results <- tibble()
  
  # Available test variables in the dataset
  available_test_vars <- intersect(indicator_config$test_vars, 
                                   names(survey_data$variables))
  
  # Available outlet variables in the dataset
  available_outlet_vars <- intersect(indicator_config$outlet_dummies, 
                                    names(survey_data$variables))
  
  for (test_var in available_test_vars) {
    for (outlet_var in available_outlet_vars) {
      
      tryCatch({
        if (is.null(group_vars)) {
          # National analysis
          subset_condition <- survey_data$variables[[outlet_var]] == 1 & 
                             !is.na(survey_data$variables[[outlet_var]]) &
                             !is.na(survey_data$variables[[test_var]])
          
          if (sum(subset_condition) > 5) {
            subset_design <- subset(survey_data, subset_condition)
            
            prop_result <- svyciprop(as.formula(paste0("~", test_var)), 
                                    subset_design,
                                    method = "logit")
            
            ci_result <- confint(prop_result, method = "logit")
            total_result <- svytotal(as.formula(paste0("~", test_var)), subset_design)
            
            result_row <- tibble(
              test_type = test_var,
              outlet_type = outlet_var,
              point_estimate = as.numeric(prop_result) * 100,
              lower_ci = ci_result[1] * 100,
              upper_ci = ci_result[2] * 100,
              n_weighted = as.numeric(total_result),
              sample_size = sum(subset_condition),
              test_label = indicator_config$test_labels[[test_var]] %||% test_var,
              outlet_label = indicator_config$outlet_labels[[outlet_var]] %||% outlet_var
            )
            
            results <- bind_rows(results, result_row)
          } else {
            # No data available
            total_outlets <- sum(survey_data$variables[[outlet_var]] == 1 & 
                               !is.na(survey_data$variables[[outlet_var]]), na.rm = TRUE)
            
            result_row <- tibble(
              test_type = test_var,
              outlet_type = outlet_var,
              point_estimate = 0,
              lower_ci = NA_real_,
              upper_ci = NA_real_,
              n_weighted = 0,
              sample_size = total_outlets,
              test_label = indicator_config$test_labels[[test_var]] %||% test_var,
              outlet_label = indicator_config$outlet_labels[[outlet_var]] %||% outlet_var
            )
            
            results <- bind_rows(results, result_row)
          }
          
        } else {
          # Strata analysis
          strata_values <- unique(survey_data$variables[[group_vars[1]]])
          strata_values <- strata_values[!is.na(strata_values)]
          
          for (strata_val in strata_values) {
            subset_condition <- survey_data$variables[[group_vars[1]]] == strata_val & 
                               survey_data$variables[[outlet_var]] == 1 & 
                               !is.na(survey_data$variables[[group_vars[1]]]) &
                               !is.na(survey_data$variables[[outlet_var]]) &
                               !is.na(survey_data$variables[[test_var]])
            
            if (sum(subset_condition) > 5) {
              subset_design <- subset(survey_data, subset_condition)
              
              prop_result <- svyciprop(as.formula(paste0("~", test_var)), 
                                      subset_design,
                                      method = "logit")
              
              ci_result <- confint(prop_result, method = "logit")
              total_result <- svytotal(as.formula(paste0("~", test_var)), subset_design)
              
              result_row <- tibble(
                test_type = test_var,
                outlet_type = outlet_var,
                point_estimate = as.numeric(prop_result) * 100,
                lower_ci = ci_result[1] * 100,
                upper_ci = ci_result[2] * 100,
                n_weighted = as.numeric(total_result),
                sample_size = sum(subset_condition),
                test_label = indicator_config$test_labels[[test_var]] %||% test_var,
                outlet_label = indicator_config$outlet_labels[[outlet_var]] %||% outlet_var
              )
              
              result_row[[group_vars[1]]] <- as.character(strata_val)
              results <- bind_rows(results, result_row)
            } else {
              # No data
              total_outlets <- sum(survey_data$variables[[group_vars[1]]] == strata_val & 
                                 survey_data$variables[[outlet_var]] == 1 &
                                 !is.na(survey_data$variables[[group_vars[1]]]) &
                                 !is.na(survey_data$variables[[outlet_var]]), na.rm = TRUE)
              
              result_row <- tibble(
                test_type = test_var,
                outlet_type = outlet_var,
                point_estimate = 0,
                lower_ci = NA_real_,
                upper_ci = NA_real_,
                n_weighted = 0,
                sample_size = total_outlets,
                test_label = indicator_config$test_labels[[test_var]] %||% test_var,
                outlet_label = indicator_config$outlet_labels[[outlet_var]] %||% outlet_var
              )
              
              result_row[[group_vars[1]]] <- as.character(strata_val)
              results <- bind_rows(results, result_row)
            }
          }
        }
        
      }, error = function(e) {
        message("Error processing ", test_var, " in ", outlet_var, ": ", e$message)
      })
    }
  }
  
  return(results)
}

# Calculate footnotes
calculate_footnotes <- function(data, strata1_var = NULL, strata2_var = NULL) {
  
  incomplete_criteria <- c(203,204,205,207,208,303,304,305,307,308,309,310)
  
  outlet_counts <- tibble()
  available_outlet_vars <- intersect(indicator_config$outlet_dummies, names(data))
  
  for (outlet_var in available_outlet_vars) {
    outlet_label <- indicator_config$outlet_labels[[outlet_var]] %||% outlet_var
    
    if (is.null(strata1_var)) {
      # National counts
      screened_count <- sum(data[[outlet_var]] == 1 & data$screened == 1, na.rm = TRUE)
      incomplete_count <- sum(data[[outlet_var]] == 1 & data$screened == 1 & 
                         data$finalintstat %in% incomplete_criteria, na.rm = TRUE)
      
      outlet_counts <- bind_rows(outlet_counts, tibble(
        outlet_type = outlet_var,
        outlet_label = outlet_label,
        screened = screened_count,
        incomplete = incomplete_count
      ))
    } else {
      # Strata counts
      strata_levels <- unique(data[[strata1_var]])
      strata_levels <- strata_levels[!is.na(strata_levels)]
      
      for (strata_val in strata_levels) {
        screened_count <- sum(data[[outlet_var]] == 1 & data$screened == 1 & 
                             data[[strata1_var]] == strata_val, na.rm = TRUE)
        incomplete_count <- sum(data[[outlet_var]] == 1 & data$screened == 1 & 
                           data[[strata1_var]] == strata_val &
                           data$finalintstat %in% incomplete_criteria, na.rm = TRUE)
        
        outlet_counts <- bind_rows(outlet_counts, tibble(
          outlet_type = outlet_var,
          outlet_label = outlet_label,
          strata = strata_val,
          screened = screened_count,
          incomplete = incomplete_count
        ))
      }
    }
  }
  
  # Format footnote
  if (is.null(strata1_var)) {
    screened_text <- paste0(outlet_counts$outlet_label, "=", outlet_counts$screened, collapse = "; ")
    incomplete_text <- paste0("Incomplete interviews = ", sum(outlet_counts$incomplete))
    return(paste0("N screened outlets: ", screened_text, ". ", incomplete_text))
  } else {
    footnotes <- list()
    strata_levels <- unique(outlet_counts$strata)
    
    for (strata_val in strata_levels) {
      strata_data <- outlet_counts %>% filter(strata == strata_val)
      screened_text <- paste0(strata_data$outlet_label, "=", strata_data$screened, collapse = "; ")
      incomplete_text <- paste0("Incomplete interviews = ", sum(strata_data$incomplete))
      footnotes[[strata_val]] <- paste0("N screened outlets: ", screened_text, ". ", incomplete_text)
    }
    return(footnotes)
  }
}
```

```{r run_analysis, include=FALSE}
# Initialize results storage
results_list <- list()
footnotes_list <- list()

# 1. National level results
national_results <- calculate_availability(survey_design)
national_footnote <- calculate_footnotes(processed_data)

results_list[["national"]] <- national_results
footnotes_list[["national"]] <- national_footnote

# 2. Strata1 results (if available)
if (has_strata1) {
 strata1_results <- calculate_availability(survey_design, group_vars = "strata1")
 
 if (nrow(strata1_results) > 0) {
   results_list[["strata1"]] <- strata1_results
   footnotes_list[["strata1"]] <- calculate_footnotes(
     processed_data, 
     strata1_var = strata_info$strata1$variable
   )
 }
}

# 3. Strata2 results (if available)
if (has_strata2) {
 strata2_results <- calculate_availability(survey_design, group_vars = "strata2")
 
 if (nrow(strata2_results) > 0) {
   results_list[["strata2"]] <- strata2_results
   footnotes_list[["strata2"]] <- calculate_footnotes(
     processed_data,
     strata2_var = strata_info$strata2$variable
   )
 }
}

# 4. Cross-stratification results (if both strata present)
if (cross_strata_possible) {
  strata1_values <- unique(survey_design$variables$strata1)
  strata1_values <- strata1_values[!is.na(strata1_values)]
  strata2_values <- unique(survey_design$variables$strata2) 
  strata2_values <- strata2_values[!is.na(strata2_values)]
  
  all_cross_results <- tibble()
  
  for (strata1_val in strata1_values) {
    for (strata2_val in strata2_values) {
      subset_condition <- survey_design$variables$strata1 == strata1_val & 
                         survey_design$variables$strata2 == strata2_val &
                         !is.na(survey_design$variables$strata1) &
                         !is.na(survey_design$variables$strata2)
      
      if (sum(subset_condition) > 10) {
        subset_design <- subset(survey_design, subset_condition)
        
        combo_results <- calculate_availability(subset_design)
        
        if (nrow(combo_results) > 0) {
          combo_results$strata1 <- strata1_val
          combo_results$strata2 <- strata2_val
          all_cross_results <- bind_rows(all_cross_results, combo_results)
        }
      }
    }
  }
  
  if (nrow(all_cross_results) > 0) {
    for (strata1_val in strata1_values) {
      strata1_data <- all_cross_results %>% filter(strata1 == strata1_val)
      if (nrow(strata1_data) > 0) {
        cross_id <- paste0("cross_", strata1_val)
        results_list[[cross_id]] <- strata1_data
        
        processed_strata1 <- processed_data %>% filter(strata1 == strata1_val)
        footnotes_list[[cross_id]] <- calculate_footnotes(processed_strata1)
      }
    }
  }
}
```

```{r create_excel_function}
# Create Excel output
source(here("Scripts", "3_Analysis", "create_excel_function.R"))

# Add antimalarial_label as alias for test_label so Excel function can parse test types
for (sheet_name in names(results_list)) {
  if (!is.null(results_list[[sheet_name]]) && nrow(results_list[[sheet_name]]) > 0) {
    results_list[[sheet_name]] <- results_list[[sheet_name]] %>%
      mutate(
        antimalarial_label = test_label,
        antimalarial_type = test_type
      )
  }
}


excel_success <- create_excel_output(
  results_list = results_list,
  footnotes_list = footnotes_list, 
  indicator_config = indicator_config,
  country = country,
  year = year,
  include_antimalarial_col = TRUE
)

if (!excel_success) {
  message("Incomplete to create Excel file")
} 
```

```{r analysis_summary, results='asis'}
cat("## Analysis Summary\n\n")
cat("**Data Processing:**\n\n")
cat("- Original outlets surveyed:", nrow(outlet_data), "\n")
cat("- Screened outlets included:", nrow(processed_data), "\n")
cat("- Survey design: Complex sampling with outlet weights\n")
cat("- Population: All screened outlets\n\n")

cat("**Stratification:**\n\n")
if (length(strata_info) > 0) {
  for (stratum_name in names(strata_info)) {
    stratum <- strata_info[[stratum_name]]
    cat("-", stratum_name, "(", length(stratum$values), "levels):", 
        paste(stratum$values, collapse = ", "), "\n")
  }
  if (cross_strata_possible) {
    cat("- Cross-stratification: Available\n")
  }
  cat("\n")
} else {
  cat("- No stratification variables available\n\n")
}

available_test_vars <- intersect(indicator_config$test_vars, names(processed_data))
available_outlet_vars <- intersect(indicator_config$outlet_dummies, names(processed_data))

cat("**Available Tests:**", length(available_test_vars), "test categories\n")
cat("**Available Outlet Types:**", length(available_outlet_vars), "outlet types\n\n")
```

## Results

### Figure 1: Test Availability by Type (National)

```{r figure_test_national, fig.width=12, fig.height=8}
if ("national" %in% names(results_list) && nrow(results_list[["national"]]) > 0) {
  
  test_by_type <- results_list[["national"]] %>%
    filter(test_type %in% indicator_config$test_types_fig) %>%
    group_by(test_type, test_label) %>%
    summarise(
      point_estimate = weighted.mean(point_estimate, sample_size, na.rm = TRUE),
      lower_ci = weighted.mean(lower_ci, sample_size, na.rm = TRUE),
      upper_ci = weighted.mean(upper_ci, sample_size, na.rm = TRUE),
      .groups = "drop"
    )
  
  if (nrow(test_by_type) > 0) {
    ggplot(test_by_type, aes(x = fct_reorder(test_label, point_estimate), 
                           y = point_estimate)) +
      geom_col(fill = "#4F81BD", alpha = 0.8) +
      geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +
      geom_text(aes(label = paste0(round(point_estimate, 1), "%")),
                hjust = -0.2, size = 3.5) +
      coord_flip() +
      labs(
        title = str_wrap("Test Availability by Type Among All Screened Outlets (National)", width = 60),
        x = "Test Type",
        y = "Percentage of Screened Outlets (%)",
        caption = "Error bars show 95% confidence intervals"
      ) +
      theme_minimal(base_size = 14) +
      theme(
        plot.title = element_text(face = "bold"),
        axis.text.y = element_text(size = 11)
      ) +
      expand_limits(y = max(test_by_type$upper_ci, na.rm = TRUE) * 1.1)
  }
}
```

### Figure 2: Test Availability by Outlet Type (National)

```{r figure_outlet_national, fig.width=12, fig.height=8}
if ("national" %in% names(results_list) && nrow(results_list[["national"]]) > 0) {
  
  any_test_by_outlet <- results_list[["national"]] %>%
    filter(test_type == "st_test")
  
  if (nrow(any_test_by_outlet) > 0) {
    ggplot(any_test_by_outlet, aes(x = fct_reorder(outlet_label, point_estimate), 
                                   y = point_estimate)) +
      geom_col(fill = "#C0504D", alpha = 0.8) +
      geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2) +
      geom_text(aes(label = paste0(round(point_estimate, 1), "%")),
                hjust = -0.2, size = 3.5) +
      coord_flip() +
      labs(
        title = str_wrap("Any Test Availability by Outlet Type Among All Screened Outlets (National)", width = 60),
        x = "Outlet Type",
        y = "Percentage with Any Test (%)",
        caption = "Error bars show 95% confidence intervals"
      ) +
      theme_minimal(base_size = 14) +
      theme(
        plot.title = element_text(face = "bold"),
        axis.text.y = element_text(size = 11)
      ) +
      expand_limits(y = max(any_test_by_outlet$upper_ci, na.rm = TRUE) * 1.1)
  }
}
```

`r if(has_strata1) "### Figure 3: Test Availability by Type and Strata1"`

```{r figure_test_type_strata1, fig.width=12, fig.height=8}
if ("strata1" %in% names(results_list) && nrow(results_list[["strata1"]]) > 0) {
  
  strata1_test_by_type <- results_list[["strata1"]] %>%
    filter(test_type %in% indicator_config$test_types_fig) %>%
    group_by(test_type, test_label, strata1) %>%
    summarise(
      point_estimate = weighted.mean(point_estimate, sample_size, na.rm = TRUE),
      lower_ci = weighted.mean(lower_ci, sample_size, na.rm = TRUE),
      upper_ci = weighted.mean(upper_ci, sample_size, na.rm = TRUE),
      .groups = "drop"
    )
  
  if (nrow(strata1_test_by_type) > 0) {
    ggplot(strata1_test_by_type, aes(x = fct_reorder(test_label, point_estimate), 
                                   y = point_estimate, fill = strata1)) +
      geom_col(position = "dodge", alpha = 0.8) +
      geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), 
                    position = position_dodge(width = 0.9), width = 0.2) +
      geom_text(aes(y = upper_ci + 2, 
                    label = paste0(round(point_estimate, 1), "%")),
                position = position_dodge(width = 0.9), hjust = 0, size = 3) +
      coord_flip() +
      labs(
        title = str_wrap("Test Availability by Type and Strata1", width = 60),
        x = "Test Type",
        y = "Percentage of Screened Outlets (%)",
        fill = "Strata1",
        caption = "Error bars show 95% confidence intervals"
      ) +
      theme_minimal(base_size = 14) +
      theme(
        plot.title = element_text(face = "bold"),
        legend.position = "bottom"
      ) +
      scale_fill_brewer(type = "qual", palette = "Set1")
  }
}
```

`r if(has_strata1) "### Figure 4: Test Availability by Outlet Type and Strata1"`

```{r figure_test_outlet_strata1, fig.width=12, fig.height=8}
if ("strata1" %in% names(results_list) && nrow(results_list[["strata1"]]) > 0) {
  
  strata1_any_test <- results_list[["strata1"]] %>%
    filter(test_type == "st_test")
  
  if (nrow(strata1_any_test) > 0) {
    ggplot(strata1_any_test, aes(x = fct_reorder(outlet_label, point_estimate), 
                               y = point_estimate, fill = strata1)) +
      geom_col(position = "dodge", alpha = 0.8) +
      geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), 
                    position = position_dodge(width = 0.9), width = 0.2) +
      geom_text(aes(y = upper_ci + 2, 
                    label = paste0(round(point_estimate, 1), "%")),
                position = position_dodge(width = 0.9), hjust = 0, size = 3) +
      coord_flip() +
      labs(
        title = str_wrap("Any Test Availability by Outlet Type and Strata1", width = 60),
        x = "Outlet Type",
        y = "Percentage with Any Test (%)",
        fill = "Strata1",
        caption = "Error bars show 95% confidence intervals"
      ) +
      theme_minimal(base_size = 14) +
      theme(
        plot.title = element_text(face = "bold"),
        legend.position = "bottom"
      ) +
      scale_fill_brewer(type = "qual", palette = "Set1")
  }
}
```

`r if(has_strata2) "### Figure 5: Test Availability by Type and Strata2"`

```{r figure_test_type_strata2, fig.width=12, fig.height=8}
if ("strata2" %in% names(results_list) && nrow(results_list[["strata2"]]) > 0) {
  
  strata2_test_by_type <- results_list[["strata2"]] %>%
    filter(test_type %in% indicator_config$test_types_fig) %>%
    group_by(test_type, test_label, strata2) %>%
    summarise(
      point_estimate = weighted.mean(point_estimate, sample_size, na.rm = TRUE),
      lower_ci = weighted.mean(lower_ci, sample_size, na.rm = TRUE),
      upper_ci = weighted.mean(upper_ci, sample_size, na.rm = TRUE),
      .groups = "drop"
    )
  
  if (nrow(strata2_test_by_type) > 0) {
    ggplot(strata2_test_by_type, aes(x = fct_reorder(test_label, point_estimate), 
                                   y = point_estimate, fill = strata2)) +
      geom_col(position = "dodge", alpha = 0.8) +
      geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), 
                    position = position_dodge(width = 0.9), width = 0.2) +
      coord_flip() +
      labs(
        title = str_wrap("Test Availability by Type and Strata2", width = 60),
        x = "Test Type",
        y = "Percentage of Screened Outlets (%)",
        fill = "Strata2",
        caption = "Error bars show 95% confidence intervals"
      ) +
      theme_minimal(base_size = 14) +
      theme(
        plot.title = element_text(face = "bold"),
        legend.position = "bottom"
      ) +
      scale_fill_brewer(type = "qual", palette = "Set2")
  }
}
```

`r if(has_strata2) "### Figure 6: Test Availability by Outlet Type and Strata2"`

```{r figure_test_outlet_strata2, fig.width=12, fig.height=8}
if ("strata2" %in% names(results_list) && nrow(results_list[["strata2"]]) > 0) {
  
  strata2_any_test <- results_list[["strata2"]] %>%
    filter(test_type == "st_test")
  
  if (nrow(strata2_any_test) > 0) {
    ggplot(strata2_any_test, aes(x = fct_reorder(outlet_label, point_estimate), 
                               y = point_estimate, fill = strata2)) +
      geom_col(position = "dodge", alpha = 0.8) +
      geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), 
                    position = position_dodge(width = 0.9), width = 0.2) +
      coord_flip() +
      labs(
        title = str_wrap("Any Test Availability by Outlet Type and Strata2", width = 60),
        x = "Outlet Type", 
        y = "Percentage with Any Test (%)",
        fill = "Strata2",
        caption = "Error bars show 95% confidence intervals"
      ) +
      theme_minimal(base_size = 14) +
      theme(
        plot.title = element_text(face = "bold"),
        legend.position = "bottom"
      ) +
      scale_fill_brewer(type = "qual", palette = "Set2")
  }
}
```

\newpage

### Table 1: National Level Results - Complete Test × Outlet Matrix

```{r table_national_complete, results='asis'}
if ("national" %in% names(results_list) && nrow(results_list[["national"]]) > 0) {
  
  point_estimates <- results_list[["national"]] %>%
    select(test_label, outlet_label, point_estimate) %>%
    arrange(test_label, outlet_label) %>%
    arrange(factor(test_label, levels = indicator_config$test_order)) %>% 
    pivot_wider(names_from = outlet_label, values_from = point_estimate, values_fill = 0) %>%
    mutate(across(where(is.numeric), ~round(., 1)))
  
  table_output <- knitr::kable(point_estimates, format = "markdown")
  cat(table_output, sep = "\n")
  cat("\n*", footnotes_list[["national"]], "*\n\n")
  
} else {
  cat("**No national level data available**\n\n")
}
```

## Technical Notes

**Survey Design:** Complex sampling with outlet weights (wt_alloutlet).

**Population:** All screened outlets (`screened == 1`), regardless of interview completion status.

**Analysis Method:** Survey-weighted proportions of outlets with specific malaria tests in stock. Each test-outlet combination analyzed separately using subpopulation methods.

**Confidence Intervals:** 95% confidence intervals calculated for proportions using logit method.

**Test Categories:**  
- **RDTs:** Rapid diagnostic tests including P. falciparum, P. vivax, and Pan-specific tests  
- **Quality Assured:** Tests meeting WHO prequalification standards  
- **Microscopy:** Microscopy testing capability  

**Excel Output:** Results exported with separate sheets for each stratification level, with detailed test-by-outlet breakdowns.

**Footnotes:** Include screened outlet counts by type and incomplete interview counts.

**Results Structure:**  
- **National:** Overall availability across all screened outlets  
- **Strata1:** Availability by primary stratification variable  
- **Strata2:** Availability by secondary stratification variable (if present)  
- **Cross-stratification:** Availability by strata2 within each level of strata1 (if both present)  

---

**Report generated:** `r format(Sys.time(), '%B %d, %Y at %I:%M %p')`
