---
title: "ACTwatch Indicator 6.2b - Purchase Price of RDTs from Suppliers (Local Currency)"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output: 
  word_document:
    toc: false
    toc_depth: 2
    reference_docx: null
---

## Indicator Definition

**Indicator Group:** Price - Purchase price of RDTs from suppliers

**Description:** The median purchase price per RDT unit from suppliers, measured in local currency, by RDT type and outlet type

**Numerator:** Median purchase price per RDT unit (local currency) for a specific RDT product/category

**Denominator:** All RDT products with purchase price data available for that product/category

**Disaggregation:** By RDT type and outlet type; additional disaggregation by strata if available

**Data Source:** Product data (long format) - includes both antimalarials and RDTs

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                      fig.width = 12, fig.height = 8)

# Set survey option to handle single PSU strata
options(survey.lonely.psu = "adjust")

library(tidyverse)
library(survey)
library(openxlsx)
library(forcats)
library(here)
library(data.table)

# Set parameters
if (!exists("country")) stop("Global variable 'country' not found")
if (!exists("year")) stop("Global variable 'year' not found") 

# Load product data (long format) to detect available RDT variables
data_file <- here("Data", "Final data", 
                  paste0(country, "_", year, "_full_data.csv"))

if (!file.exists(data_file)) {
  stop("Data file not found: ", data_file)
}

product_data_temp <- fread(data_file) %>%
  rename_with(tolower)

# Dynamically detect RDT manufacturer variables and their labels
# This ensures the analysis works across different countries/survey rounds

# Start with base RDT variables
rdt_vars <- c("rdt_true", "qardt")
rdt_labels <- list(
  "rdt_true" = "RDT audited is true RDT",
  "qardt" = "WHO PQ RDT"
)

# Detect manufacturer dummy variables (rdtmanu_1, rdtmanu_2, rdtmanu_3, etc.)
manu_vars <- names(product_data_temp)[grepl("^rdtmanu_[0-9]+$", names(product_data_temp))]

if (length(manu_vars) > 0 && "rdtmanu" %in% names(product_data_temp)) {
  # Extract manufacturer labels from data
  mfr_mapping <- product_data_temp %>%
    filter(!is.na(rdtmanu)) %>%
    select(rdtmanu, all_of(manu_vars)) %>%
    pivot_longer(cols = all_of(manu_vars), 
                 names_to = "var", 
                 values_to = "value") %>%
    filter(value == 1) %>%
    distinct(var, rdtmanu) %>%
    arrange(var)
  
  # Add manufacturer variables to rdt_vars and labels
  for (i in 1:nrow(mfr_mapping)) {
    var_name <- mfr_mapping$var[i]
    mfr_name <- mfr_mapping$rdtmanu[i]
    
    rdt_vars <- c(rdt_vars, var_name)
    rdt_labels[[var_name]] <- paste0("RDT manufacturer: ", mfr_name)
  }
  
  cat("Found", length(manu_vars), "manufacturer variables:\n")
  print(mfr_mapping)
} else {
  cat("No manufacturer variables found or rdtmanu variable missing\n")
}

# Clean up temporary data
rm(product_data_temp)

# Configuration matching the Stata analysis structure
indicator_config <- list(
  indicator_id = "6.2b",
  title = "Purchase Price of RDTs from Suppliers (Local Currency)", 
  description = "Median purchase price per RDT unit from suppliers by type and outlet",
  
  # Analysis settings
  dataset = "product", # Product data in long format (includes both AMs and RDTs)
  analysis_type = "price",
  survey_weight = "wt_alloutlet", # Standard outlet weight for price analysis
  price_variable = "unitrdtwholeprice", # Purchase price per RDT unit in local currency
  population_filter = quote(countprod == 1), # Counted products (includes both anyam==1 and rdt_true==1)
  
  # Outlet types (matching Stata outvars1)
  outlet_dummies = c("private_nonprofit", "private_forprofit", "pharmacy",
                    "laboratory", "drug_store", "total_informal", "total_retail", "wholesale"),
  outlet_labels = list(
    "private_nonprofit" = "Private Not-for-Profit",
    "private_forprofit" = "Private For-Profit", 
    "pharmacy" = "Pharmacy",
    "laboratory" = "Laboratory", 
    "drug_store" = "Drug Store",
    "total_informal" = "Informal (Total)",
    "total_retail" = "Retail (Total)",
    "wholesale" = "Wholesaler"
  ),

  # RDT products - dynamically detected above
  rdt_vars = rdt_vars,
  rdt_labels = rdt_labels,
  rdt_order = rdt_vars,
  
  # Output settings
  file_suffix = "Purchase price of RDTs from suppliers-local currency"
)

cat("\nFinal RDT variables to analyze:\n")
for (i in seq_along(indicator_config$rdt_vars)) {
  var_name <- indicator_config$rdt_vars[i]
  var_label <- indicator_config$rdt_labels[[var_name]]
  cat(sprintf("%d. %s: %s\n", i, var_name, var_label))
}

# Source the create_excel_function (if available)
excel_function_path <- here("Scripts", "3_Analysis", "create_excel_function.R")
if (file.exists(excel_function_path)) {
  source(excel_function_path)
}
```

```{r load_data, include=FALSE}
# Load product data (long format)
data_file <- here("Data", "Final data", 
                  paste0(country, "_", year, "_full_data.csv"))

if (!file.exists(data_file)) {
  stop("Data file not found: ", data_file)
}

product_data <- fread(data_file) %>%
  # Convert all variable names to lowercase for consistency
  rename_with(tolower) %>%
  # Ensure strata variables are character
  mutate(across(any_of(c("strata1", "strata2")), as.character)) %>%
  # Clean up blank but non-missing strata values
  mutate(
    strata1 = dplyr::na_if(strata1, ""),
    strata2 = dplyr::na_if(strata2, "")
  ) %>%
  # Drop if outlet category information is missing (following Stata logic)
  filter(!is.na(outcat2))
```

```{r data_processing, include=FALSE}
# Following Stata logic: ensuring RDTs included
# countprod=1 if anyAM==1; recode countprod (.=1) if rdt_true==1
product_data <- product_data %>%
  mutate(
    countprod = case_when(
      anyam == 1 ~ 1,
      rdt_true == 1 ~ 1,
      TRUE ~ 0
    )
  )

# Following Stata logic: ensure outlet variables are coded as 0/1
available_outlet_vars <- intersect(indicator_config$outlet_dummies, names(product_data))

# Recode outlet variables (following Stata: recode `x'(.=0) if countprod==1)
product_data <- product_data %>%
  mutate(
    across(all_of(available_outlet_vars), 
           ~ifelse(is.na(.) & countprod == 1, 0, .))
  )

# Apply population filter (counted products)
base_data <- product_data %>%
  filter(!!indicator_config$population_filter)

# Detect available RDT variables in the data
available_rdt_vars <- intersect(indicator_config$rdt_vars, names(base_data))
if (length(available_rdt_vars) == 0) {
  stop("No RDT variables found in data. Expected variables: ", 
       paste(indicator_config$rdt_vars, collapse = ", "))
}

# Detect strata structure
strata_info <- list()
if ("strata1" %in% names(base_data) && 
    length(unique(na.omit(base_data$strata1))) > 1) {
  strata1_values <- unique(na.omit(base_data$strata1))
  strata1_values <- strata1_values[strata1_values != "" & !is.na(trimws(strata1_values))]
  if (length(strata1_values) > 1) {
    strata_info$strata1 <- list(variable = "strata1", values = strata1_values)
  }
}

if ("strata2" %in% names(base_data) && 
    length(unique(na.omit(base_data$strata2))) > 1) {
  strata2_values <- unique(na.omit(base_data$strata2))
  strata2_values <- strata2_values[strata2_values != "" & !is.na(trimws(strata2_values))]
  if (length(strata2_values) > 1) {
    strata_info$strata2 <- list(variable = "strata2", values = strata2_values)
  }
}

has_strata1 <- "strata1" %in% names(strata_info)
has_strata2 <- "strata2" %in% names(strata_info)
cross_strata_possible <- has_strata1 && has_strata2
```

```{r analysis_function, include=FALSE}
# Function to calculate prices for a specific RDT product and outlet combination
analyze_rdt_prices <- function(data, rdt_var, outlet_vars, price_var, survey_weight, 
                               strata_var = NULL, strata_values = NULL) {
  
  # Check if variables exist
  if (!rdt_var %in% names(data)) {
    warning(paste("RDT variable", rdt_var, "not found"))
    return(NULL)
  }
  if (!price_var %in% names(data)) {
    warning(paste("Price variable", price_var, "not found"))
    return(NULL)
  }
  
  # Filter for this RDT type and non-missing prices
  rdt_data <- data %>%
    filter(!!sym(rdt_var) == 1 & !is.na(!!sym(price_var)))
  
  if (nrow(rdt_data) == 0) {
    return(NULL)
  }
  
  # Apply strata filter if specified
  if (!is.null(strata_var) && !is.null(strata_values)) {
    if (length(strata_values) == 1) {
      rdt_data <- rdt_data %>%
        filter(!!sym(strata_var) == strata_values)
    }
  }
  
  if (nrow(rdt_data) == 0) {
    return(NULL)
  }
  
  # Setup survey design
  rdt_data_filtered <- rdt_data %>%
    filter(!is.na(!!sym(survey_weight)))
  
  # Check if we have enough PSUs for survey design
  n_psu <- rdt_data_filtered %>% 
    summarise(n_psu = n_distinct(c4, na.rm = TRUE)) %>% 
    pull(n_psu)
  
  if (n_psu < 2) {
    message(paste("Skipping", rdt_var, "- insufficient PSUs (n =", n_psu, ")"))
    return(NULL)
  }
  
  survey_design <- tryCatch({
    rdt_data_filtered %>%
      as_survey_design(
        ids = c4,
        weights = !!sym(survey_weight),
        strata = strata1,
        fpc = fpc
      )
  }, error = function(e) {
    message(paste("Error creating survey design for", rdt_var, ":", e$message))
    return(NULL)
  })
  
  if (is.null(survey_design)) {
    return(NULL)
  }
  
  results <- tibble()
  
  # Calculate prices for each outlet type
  for (outlet in outlet_vars) {
    if (!outlet %in% names(rdt_data)) next
    
    outlet_data <- survey_design %>%
      filter(!!sym(outlet) == 1)
    
    if (nrow(outlet_data) == 0) next
    
    # Calculate weighted percentiles
    tryCatch({
      # Try using statar package if available
      if (requireNamespace("statar", quietly = TRUE)) {
        pctiles <- outlet_data %>%
          summarise(
            q25 = statar::pctile(!!sym(price_var), probs = 0.25, w = !!sym(survey_weight)),
            q50 = statar::pctile(!!sym(price_var), probs = 0.50, w = !!sym(survey_weight)),
            q75 = statar::pctile(!!sym(price_var), probs = 0.75, w = !!sym(survey_weight)),
            n = n()
          )
      } else {
        # Fallback to survey package
        pctiles <- tibble(
          q25 = as.numeric(svyquantile(as.formula(paste0("~", price_var)), 
                                       outlet_data, quantiles = 0.25, na.rm = TRUE)),
          q50 = as.numeric(svyquantile(as.formula(paste0("~", price_var)), 
                                       outlet_data, quantiles = 0.50, na.rm = TRUE)),
          q75 = as.numeric(svyquantile(as.formula(paste0("~", price_var)), 
                                       outlet_data, quantiles = 0.75, na.rm = TRUE)),
          n = nrow(outlet_data)
        )
      }
      
      result_row <- tibble(
        rdt_type = rdt_var,
        antimalarial_label = indicator_config$rdt_labels[[rdt_var]] %||% rdt_var,
        outlet_type = outlet,
        outlet_label = indicator_config$outlet_labels[[outlet]] %||% outlet,
        point_estimate = pctiles$q50,
        lower_ci = pctiles$q25,
        upper_ci = pctiles$q75,
        sample_size = pctiles$n
      )
      
      if (!is.null(strata_var)) {
        if (length(strata_values) == 1) {
          result_row[[strata_var]] <- strata_values
        }
      }
      
      results <- bind_rows(results, result_row)
    }, error = function(e) {
      message(paste("Error calculating percentiles for", outlet, ":", e$message))
    })
  }
  
  return(results)
}

# Function to calculate footnotes
calculate_footnotes <- function(data, price_var) {
  # Count outlets that met screening but didn't complete full interview
  incomplete_interviews <- data %>%
    filter(finalintstat %in% c(203, 204, 205, 207, 208, 303, 304, 305, 307, 308, 309, 310) & 
           anyam == 1) %>%
    nrow()
  
  # Count products missing price data
  missing_prices <- data %>%
    filter(anyam == 1 & is.na(!!sym(price_var))) %>%
    nrow()
  
  paste0("N outlets that met screening criteria but did not complete full interview: ", 
         incomplete_interviews, 
         "; N RDT products audited but missing price information: ", 
         missing_prices)
}
```

```{r run_analysis, include=FALSE}
# Initialize results storage
results_list <- list()
footnotes_list <- list()

# Calculate overall footnote
overall_footnote <- calculate_footnotes(base_data, indicator_config$price_variable)

# Analyze each RDT type
for (rdt_var in available_rdt_vars) {
  
  # National level
  national_results <- analyze_rdt_prices(
    base_data, rdt_var, available_outlet_vars, 
    indicator_config$price_variable, indicator_config$survey_weight
  )
  
  if (!is.null(national_results) && nrow(national_results) > 0) {
    if (!"national" %in% names(results_list)) {
      results_list[["national"]] <- tibble()
    }
    results_list[["national"]] <- bind_rows(results_list[["national"]], national_results)
  }
  
  # Strata1 level
  if (has_strata1) {
    for (strata_val in strata_info$strata1$values) {
      strata1_results <- analyze_rdt_prices(
        base_data, rdt_var, available_outlet_vars, 
        indicator_config$price_variable, indicator_config$survey_weight,
        strata_var = "strata1", strata_values = strata_val
      )
      
      if (!is.null(strata1_results) && nrow(strata1_results) > 0) {
        if (!"strata1" %in% names(results_list)) {
          results_list[["strata1"]] <- tibble()
        }
        results_list[["strata1"]] <- bind_rows(results_list[["strata1"]], strata1_results)
      }
    }
  }
  
  # Strata2 level
  if (has_strata2) {
    for (strata_val in strata_info$strata2$values) {
      strata2_results <- analyze_rdt_prices(
        base_data, rdt_var, available_outlet_vars, 
        indicator_config$price_variable, indicator_config$survey_weight,
        strata_var = "strata2", strata_values = strata_val
      )
      
      if (!is.null(strata2_results) && nrow(strata2_results) > 0) {
        if (!"strata2" %in% names(results_list)) {
          results_list[["strata2"]] <- tibble()
        }
        results_list[["strata2"]] <- bind_rows(results_list[["strata2"]], strata2_results)
      }
    }
  }
  
  # Cross-stratification
  if (cross_strata_possible) {
    for (s1_val in strata_info$strata1$values) {
      for (s2_val in strata_info$strata2$values) {
        cross_data <- base_data %>%
          filter(strata1 == s1_val & strata2 == s2_val)
        
        if (nrow(cross_data) > 0) {
          cross_results <- analyze_rdt_prices(
            cross_data, rdt_var, available_outlet_vars, 
            indicator_config$price_variable, indicator_config$survey_weight
          )
          
          if (!is.null(cross_results) && nrow(cross_results) > 0) {
            cross_results <- cross_results %>%
              mutate(strata1 = s1_val, strata2 = s2_val)
            
            cross_name <- paste0("cross_", s1_val)
            if (!cross_name %in% names(results_list)) {
              results_list[[cross_name]] <- tibble()
            }
            results_list[[cross_name]] <- bind_rows(results_list[[cross_name]], cross_results)
          }
        }
      }
    }
  }
}

# Set footnotes for all sheets
for (sheet_name in names(results_list)) {
  footnotes_list[[sheet_name]] <- overall_footnote
}
```

```{r export_excel, include=FALSE}
# Use the standard create_excel_output function
excel_success <- create_excel_output(
  results_list = results_list,
  footnotes_list = footnotes_list, 
  indicator_config = indicator_config,
  country = country,
  year = year,
  include_antimalarial_col = TRUE
)

if (excel_success) {
  cat("Excel file created successfully\n")
} else {
  cat("Warning: Excel file creation encountered issues\n")
}
```

\newpage

## Executive Summary

This indicator analyzes the median purchase prices of Rapid Diagnostic Tests (RDTs) from suppliers, measured in local currency. The analysis covers:

- **Any RDT:** All RDT products
- **Quality Assured RDTs:** RDTs meeting quality assurance standards

Results are disaggregated by outlet type and, where applicable, by geographic or administrative strata.

**Key Findings:**

```{r summary_stats, results='asis'}
if ("national" %in% names(results_list) && nrow(results_list[["national"]]) > 0) {
  
  # Summarize by RDT type
  summary_by_rdt <- results_list[["national"]] %>%
    group_by(antimalarial_label) %>%
    summarise(
      median_price = median(point_estimate, na.rm = TRUE),
      min_price = min(point_estimate, na.rm = TRUE),
      max_price = max(point_estimate, na.rm = TRUE),
      outlets_offering = n(),
      .groups = "drop"
    ) %>%
    arrange(desc(median_price))
  
  cat("\n**RDT Purchase Price Summary (Local Currency):**\n\n")
  for (i in 1:nrow(summary_by_rdt)) {
    cat(paste0("- **", summary_by_rdt$antimalarial_label[i], ":** ", 
               "Median = ", round(summary_by_rdt$median_price[i], 2), " LCU",
               " (range: ", round(summary_by_rdt$min_price[i], 2), 
               " to ", round(summary_by_rdt$max_price[i], 2), " LCU)\n"))
  }
  
} else {
  cat("**No national level data available**\n\n")
}
```

\newpage

## Figures

### Figure 1: RDT Purchase Prices by Type (National Level)

```{r figure_national_prices, fig.width=12, fig.height=8}
if ("national" %in% names(results_list) && nrow(results_list[["national"]]) > 0) {
  
  # Calculate median across outlets for each RDT type
  national_rdt_prices <- results_list[["national"]] %>%
    group_by(antimalarial_label) %>%
    summarise(
      median_price = weighted.mean(point_estimate, sample_size, na.rm = TRUE),
      q25 = weighted.mean(lower_ci, sample_size, na.rm = TRUE),
      q75 = weighted.mean(upper_ci, sample_size, na.rm = TRUE),
      .groups = "drop"
    )
  
  if (nrow(national_rdt_prices) > 0) {
    ggplot(national_rdt_prices, aes(x = reorder(antimalarial_label, median_price), 
                                     y = median_price)) +
      geom_col(fill = "#2171b5", alpha = 0.8) +
      geom_errorbar(aes(ymin = q25, ymax = q75), width = 0.3) +
      coord_flip() +
      labs(
        title = "Median RDT Purchase Prices by Type (National Level)",
        x = "RDT Type",
        y = "Median Purchase Price (Local Currency)",
        caption = "Error bars show interquartile range (Q25-Q75)"
      ) +
      theme_minimal(base_size = 14) +
      theme(
        plot.title = element_text(face = "bold"),
        axis.text = element_text(size = 12)
      ) +
      scale_y_continuous(expand = expansion(mult = c(0, 0.15)))
  }
}
```

### Figure 2: RDT Purchase Prices by Outlet Type (National Level)

```{r figure_outlet_prices, fig.width=12, fig.height=10}
if ("national" %in% names(results_list) && nrow(results_list[["national"]]) > 0) {
  
  ggplot(results_list[["national"]], 
         aes(x = fct_reorder(outlet_label, point_estimate), 
             y = point_estimate, fill = antimalarial_label)) +
    geom_col(position = "dodge", alpha = 0.8) +
    geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), 
                  position = position_dodge(width = 0.9), width = 0.2) +
    coord_flip() +
    labs(
      title = "Median RDT Purchase Prices by Outlet Type and RDT Type",
      x = "Outlet Type",
      y = "Median Purchase Price (Local Currency)",
      fill = "RDT Type",
      caption = "Error bars show interquartile range (Q25-Q75)"
    ) +
    theme_minimal(base_size = 14) +
    theme(
      plot.title = element_text(face = "bold"),
      legend.position = "bottom",
      legend.text = element_text(size = 10)
    ) +
    scale_fill_brewer(type = "qual", palette = "Set2") +
    scale_y_continuous(expand = expansion(mult = c(0, 0.15)))
}
```

`r if(has_strata1) "### Figure 3: RDT Purchase Prices by Type and Strata1"`

```{r figure_rdt_prices_strata1, fig.width=12, fig.height=8}
if ("strata1" %in% names(results_list) && nrow(results_list[["strata1"]]) > 0) {
  
  strata1_rdt_prices <- results_list[["strata1"]] %>%
    group_by(antimalarial_label, strata1) %>%
    summarise(
      median_price = weighted.mean(point_estimate, sample_size, na.rm = TRUE),
      q25 = weighted.mean(lower_ci, sample_size, na.rm = TRUE),
      q75 = weighted.mean(upper_ci, sample_size, na.rm = TRUE),
      .groups = "drop"
    )
  
  if (nrow(strata1_rdt_prices) > 0) {
    ggplot(strata1_rdt_prices, aes(x = reorder(antimalarial_label, median_price), 
                                    y = median_price, fill = strata1)) +
      geom_col(position = "dodge", alpha = 0.8) +
      geom_errorbar(aes(ymin = q25, ymax = q75), 
                    position = position_dodge(width = 0.9), width = 0.2) +
      coord_flip() +
      labs(
        title = "Median RDT Purchase Prices by Type and Strata1",
        x = "RDT Type",
        y = "Median Purchase Price (Local Currency)",
        fill = "Strata1",
        caption = "Error bars show interquartile range (Q25-Q75)"
      ) +
      theme_minimal(base_size = 14) +
      theme(
        plot.title = element_text(face = "bold"),
        legend.position = "bottom"
      ) +
      scale_fill_brewer(type = "qual", palette = "Set1") +
      scale_y_continuous(expand = expansion(mult = c(0, 0.15)))
  }
}
```

`r if(has_strata2) "### Figure 4: RDT Purchase Prices by Type and Strata2"`

```{r figure_rdt_prices_strata2, fig.width=12, fig.height=8}
if ("strata2" %in% names(results_list) && nrow(results_list[["strata2"]]) > 0) {
  
  strata2_rdt_prices <- results_list[["strata2"]] %>%
    group_by(antimalarial_label, strata2) %>%
    summarise(
      median_price = weighted.mean(point_estimate, sample_size, na.rm = TRUE),
      q25 = weighted.mean(lower_ci, sample_size, na.rm = TRUE),
      q75 = weighted.mean(upper_ci, sample_size, na.rm = TRUE),
      .groups = "drop"
    )
  
  if (nrow(strata2_rdt_prices) > 0) {
    ggplot(strata2_rdt_prices, aes(x = reorder(antimalarial_label, median_price), 
                                    y = median_price, fill = strata2)) +
      geom_col(position = "dodge", alpha = 0.8) +
      geom_errorbar(aes(ymin = q25, ymax = q75), 
                    position = position_dodge(width = 0.9), width = 0.2) +
      coord_flip() +
      labs(
        title = "Median RDT Purchase Prices by Type and Strata2",
        x = "RDT Type",
        y = "Median Purchase Price (Local Currency)",
        fill = "Strata2",
        caption = "Error bars show interquartile range (Q25-Q75)"
      ) +
      theme_minimal(base_size = 14) +
      theme(
        plot.title = element_text(face = "bold"),
        legend.position = "bottom"
      ) +
      scale_fill_brewer(type = "qual", palette = "Set2") +
      scale_y_continuous(expand = expansion(mult = c(0, 0.15)))
  }
}
```

\newpage

## Tables

### Table 1: National Level Results - Prices by RDT Type × Outlet Matrix

```{r table_national_price, results='asis'}
if ("national" %in% names(results_list) && nrow(results_list[["national"]]) > 0) {
  
  # Create comprehensive table with median prices as values
  price_matrix <- results_list[["national"]] %>%
    select(antimalarial_label, outlet_label, point_estimate) %>%
    pivot_wider(names_from = outlet_label, values_from = point_estimate, values_fill = NA) %>%
    mutate(across(where(is.numeric), ~round(., 2)))
  
  table_output <- knitr::kable(price_matrix, format = "markdown",
                              caption = "Median Purchase Price (Local Currency)")
  cat(table_output, sep = "\n")
  cat("\n")
  
  # Add footnote
  cat("\n**Footnote:**\n\n")
  cat("*", overall_footnote, "*\n\n")
  
} else {
  cat("**No national level data available**\n\n")
}
```

`r if(has_strata1) "### Table 2: Strata1 Level Results"`

```{r table_strata1_price, results='asis'}
if ("strata1" %in% names(results_list) && nrow(results_list[["strata1"]]) > 0) {
  
  for (strata_val in strata_info$strata1$values) {
    cat("\n#### ", strata_val, "\n\n")
    
    strata_data <- results_list[["strata1"]] %>%
      filter(strata1 == strata_val)
    
    if (nrow(strata_data) > 0) {
      price_matrix <- strata_data %>%
        select(antimalarial_label, outlet_label, point_estimate) %>%
        pivot_wider(names_from = outlet_label, values_from = point_estimate, values_fill = NA) %>%
        mutate(across(where(is.numeric), ~round(., 2)))
      
      table_output <- knitr::kable(price_matrix, format = "markdown",
                                  caption = paste("Median Purchase Price (Local Currency) -", strata_val))
      cat(table_output, sep = "\n")
      cat("\n")
    }
  }
}
```

\newpage

## Technical Notes

**Survey Design:** Complex sampling with outlet weights (`wt_alloutlet`), cluster sampling (c4), stratification (strata1), and finite population correction (fpc).

**Population Filter:** Analysis limited to:  
- Counted products (`countprod == 1`) which includes both antimalarials (`anyam == 1`) and RDTs (`rdt_true == 1`)
- Products with non-missing purchase price data  

**Data Source:** Full product data (`${country}_${year}_full_data`) containing both antimalarials and RDTs

**Price Variable:** `unitrdtwholeprice` - Purchase price per RDT unit from suppliers in local currency

**RDT Types Analyzed:**

1. **Any RDT** (`rdt_true`): All RDT products regardless of quality status
2. **Quality Assured RDT** (`qardt`): RDTs meeting quality assurance standards

**Statistical Method:** Survey-weighted quantiles (25th, 50th, and 75th percentiles) using `statar::pctile()` for weighted percentiles, with fallback to `survey` package's `svyquantile()`.

**Results Structure:**  
- **National:** Overall purchase price medians across all outlets with price data
- **Strata1:** Purchase price medians by primary stratification variable (if present and varies)  
- **Strata2:** Purchase price medians by secondary stratification variable (if present and varies)  
- **Cross-stratification:** Purchase price medians by strata2 within each level of strata1 (if both strata present)  

**Flexible Stratification:** Unlike the original Stata code which hardcoded urban/rural categories, this R version:  
- Uses generic `strata1` and `strata2` variable names  
- Automatically detects available strata values  
- Adapts to whatever stratification structure exists in your data  
- Works with any stratification scheme (e.g., region, province, urban/rural)  

**Excel Output:** Results exported to Excel workbook with separate sheets for each analysis level. Each RDT type generates its own set of results across outlet types. Median prices appear as "Point Estimate" and quartiles as "Lower CI"/"Upper CI" for consistency with other indicators.

**Footnotes:** Include:
1. Count of outlets that met screening criteria but didn't complete full interview
2. Count of RDT products audited but missing price information

**Data Standardization:** Results use common column structure (`rdt_type`, `antimalarial_label`, `outlet_type`, `point_estimate`, `lower_ci`, `upper_ci`) where:  
- `point_estimate` = median purchase price (local currency)  
- `lower_ci` = 25th percentile (Q25)  
- `upper_ci` = 75th percentile (Q75)  
- Note: `antimalarial_label` is used for consistency with Excel output function, but contains RDT type labels

**Key Differences from Indicator 6.1b:**  
- **6.1b** measures antimalarial purchase prices per AETD (tablet formulations only)
- **6.2b** measures RDT purchase prices per unit (all RDT products)
- Both use local currency and same analysis structure
- 6.2b includes both antimalarials and RDTs in `countprod` definition

**Comparison with Sales Price Indicators:**
- Purchase price (6.2b) = what suppliers charge outlets
- Sales price (5.3b if it exists) = what outlets charge customers
- The difference represents markup/margin

**Survey Design Notes:**
- Uses `options(survey.lonely.psu = "adjust")` to handle strata with single PSUs
- Includes error handling for RDT/outlet combinations with insufficient clusters
- Skips combinations that cannot support variance estimation

---

**Report generated:** `r format(Sys.time(), '%B %d, %Y at %I:%M %p')`
